---
title: "proGresAnalysis functions"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
knitr::opts_chunk$set(
                      comment = "#>",
                      message=FALSE, 
                      warning=FALSE,
                      #fig.retina = 2, 
                      fig.width = 8,
                      fig.asp = 0.618,
                     # fig.align = "center",
                     # dev = "ragg_png",
                      out.width = "90%"
)
unlink(".RData")
library(testthat)
library(ggplot2)
library(unhcrthemes)
# library(extrafont) 
# font_import()
# loadfonts()
# font_install('fontcm')
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 




## Data examples to demo the package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

The included demo was created to display how the plotting functions works



```{r development-dataset}
# Run all this chunk in the console directly
# Create "inst/" directory
#dir.create(here::here("inst"))

# Example dataset
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows

## load all data  assuming they are located in a  `data-raw` within your Rstudio project
# progresobj <- list(
#     Individual <- readr::read_csv(system.file("demo/Individual.csv", package = "proGresAnalysis") ), 
#     
#     RegistrationGroup <- readr::read_csv(system.file("demo/RegistrationGroup.csv", package = "proGresAnalysis") ) ,
#     
#     Assistance <- readr::read_csv(system.file("demo/Assistance.csv", package = "proGresAnalysis") , progress = TRUE) ,
#     #Assistance <- utils::read.csv(system.file("Assistance.csv", package = "proGresAnalysis") , encoding = "UTF-8", na.strings = "") 
#     #Assistance <- utils::read.csv(system.file("Assistance.csv", package = "proGresAnalysis") ) 
#     
#     Document <- readr::read_csv(system.file("demo/Document.csv", package = "proGresAnalysis") ) ,
#     
#     Education <- readr::read_csv(system.file("demo/Education.csv", package = "proGresAnalysis") ) ,
#     
#     EntitlementCard <- readr::read_csv(system.file("demo/EntitlementCard.csv", package = "proGresAnalysis") ) ,
#     
#     IndividualProperty <- readr::read_csv(system.file("demo/IndividualProperty.csv", package = "proGresAnalysis") ), 
#     
#     Language <- readr::read_csv(system.file("demo/Language.csv", package = "proGresAnalysis") ) ,
#     
#     Nationality <- readr::read_csv(system.file("demo/Nationality.csv", package = "proGresAnalysis") ) ,
#     
#     Relative <- readr::read_csv(system.file("demo/Relative.csv", package = "proGresAnalysis") ) ,
#     
#     Representative <- readr::read_csv(system.file("demo/Representative.csv", package = "proGresAnalysis") ), 
#     
#     Skill <- readr::read_csv(system.file("demo/Skill.csv", package = "proGresAnalysis") ) ,
#     
#     SocioEconomic <- readr::read_csv(system.file("demo/SocioEconomic.csv", package = "proGresAnalysis") ) ,
#     
#     SpecificNeed <- readr::read_csv(system.file("demo/SpecificNeed.csv", package = "proGresAnalysis") ), 
#     #SpecificNeed <- utils::read.csv(system.file("demo/SpecificNeed.csv"), encoding = "UTF-8", na.strings = "") 
#     
#     Transit <- readr::read_csv(system.file("demo/Transit.csv", package = "proGresAnalysis") ) ,
#     
#     WorkExperience <- readr::read_csv(system.file("demo/WorkExperience.csv", package = "proGresAnalysis"), 
#         ## some encoding issue to address... it's not expected UTF-8..
#         locale = readr::locale(encoding = "UTF-16")) 
#  )

```


## data_get
<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function-data_get}
#' @title get data from RIDL
#'
#' @param ridldataset name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @param dataraw folder where to put the data
#'
#' @export 

data_get <- function(ridldataset,
                     dataraw = "data-raw") {
  # remotes::install_gitlab("dickoa/ridl")
  ## Note that you need to set up your environment variable first
  require(ridl)
 #  ridl::ridl_config_get()
 #  
 #  library(tidyverse)
 #  ridl::ridl_dataset_search("registration") 
 ridldatasets <- ridl::ridl_dataset_show(ridldataset)
  
 # Create "data-raw" folder if it does not exist
 if (!dir.exists(here::here(dataraw))) {dir.create(here::here(dataraw))}
 # And now get all ressources there
 lapply(ridl::ridl_dataset_resource_get_all(ridldatasets),
        \(r) 
        ridl::ridl_resource_download(r, 
                                     folder = here::here(dataraw)) )
 ## get all the zip files and unzip them in the same folder
 filelist <- list.files(here::here(dataraw), pattern = ".zip", recursive = F)
 plyr::ldply(.data = here::here(dataraw,filelist), .fun = unzip,
             exdir = here::here(dataraw))
}
 
```


```{r examples-data_get}

# data_get(ridldataset = "xxxx", dataraw = "data-raw")

```

## data_load
<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function-data_load}
#' @title get data from RIDL
#'
#' @param dataraw folder where to put the data
#' @return  progresobj  a list with all required frame
#'
#' @export 

data_load <- function(dataraw = "data-raw" ) {
 
     Individual <- readr::read_csv(here::here(dataraw, "Individual.csv"))
 
     RegistrationGroup <- readr::read_csv(here::here(dataraw, "RegistrationGroup.csv")) 
  
    # Address <- readr::read_csv(here::here(dataraw, "Address.csv"), progress = TRUE) 
     Assistance <- readr::read_csv(here::here(dataraw, "Assistance.csv"), progress = TRUE) 
     #Assistance <- utils::read.csv(here::here(dataraw, "Assistance.csv"), encoding = "UTF-8", na.strings = "") 
     #Assistance <- utils::read.csv(here::here(dataraw, "Assistance.csv")) 
  
     Document <- readr::read_csv(here::here(dataraw, "Document.csv")) 
  
     Education <- readr::read_csv(here::here(dataraw, "Education.csv"))
  
    EntitlementCard <- readr::read_csv(here::here(dataraw, "EntitlementCard.csv")) 
    
    IndividualProperty <- readr::read_csv(here::here(dataraw, "IndividualProperty.csv"))
    
    Language <- readr::read_csv(here::here(dataraw, "Language.csv"))
    
    Nationality <- readr::read_csv(here::here(dataraw, "Nationality.csv")) 
    
    Relative <- readr::read_csv(here::here(dataraw, "Relative.csv"))
    
    Representative <- readr::read_csv(here::here(dataraw, "Representative.csv"))
    
    Skill <- readr::read_csv(here::here(dataraw, "Skill.csv"))
    
    SocioEconomic <- readr::read_csv(here::here(dataraw, "SocioEconomic.csv"))
    
    SpecificNeed <- readr::read_csv(here::here(dataraw, "SpecificNeed.csv")) 
    #SpecificNeed <- utils::read.csv(here::here(dataraw, "SpecificNeed.csv"), encoding = "UTF-8", na.strings = "") 
    
    Transit <- readr::read_csv(here::here(dataraw, "Transit.csv")) 
    
    WorkExperience <- readr::read_csv(here::here(dataraw, "WorkExperience.csv"), 
        ## some encoding issue to addres... it's not expected UTF-8..
        locale = readr::locale(encoding = "UTF-16"))
  
 
 progresobj <- list(
     Individual,
     RegistrationGroup,
     Assistance, 
     Document,
     Education , 
    EntitlementCard,
    IndividualProperty , 
    Language , 
    Nationality ,
    Relative , 
    Representative, 
    Skill, 
    SocioEconomic ,
    SpecificNeed ,
    Transit ,
    WorkExperience  )
 
    rm(
     Individual,
     RegistrationGroup,
     Assistance, 
     Document,
     Education , 
    EntitlementCard,
    IndividualProperty , 
    Language , 
    Nationality ,
    Relative , 
    Representative, 
    Skill, 
    SocioEconomic ,
    SpecificNeed ,
    Transit ,
    WorkExperience  )
    return(progresobj)

     
     ## remotes::install_github("galalH/riddle")
     # library("riddle")
     # url <- "https://ridl.unhcr.org/dataset/brazil-registration-data-february-2022"
     # 
     # riddle::resource_fetch(url, path = here::here("data-raw2"))
}

```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples-data_load}

#progresobj <- data_load(dataraw = "data-raw")

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )


```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests-data_load}


```

 
 
## data_recode

```{r function-data_recode}
#' @title Assemble all data components in a list and compute indicators
#' @param progresobj  a list with all required frame
#' @param ctr Country or Business Unit for the dataset dump
#' @return progresobjexpand  a list with all required frame
#' 
#' @export 

data_recode <- function(progresobj, ctr ) {
  
  require(tidyverse)
    ## Deconstruct the list... 
    Individual <- as.data.frame(progresobj[1] ) 
    RegistrationGroup <- as.data.frame(progresobj[2] )
    Assistance <-  as.data.frame(progresobj[3] )
    Document <-  as.data.frame(progresobj[4] )
    Education <-  as.data.frame(progresobj[5] )
    EntitlementCard <-  as.data.frame(progresobj[6]) 
    IndividualProperty <-  as.data.frame(progresobj[7]) 
    Language <-  as.data.frame(progresobj[8] )
    Nationality <-  as.data.frame(progresobj[9]) 
    Relative <-  as.data.frame(progresobj[10] )
    Representative <-  as.data.frame(progresobj[11]) 
    Skill <-  as.data.frame(progresobj[12] )
    SocioEconomic <-  as.data.frame(progresobj[13]) 
    SpecificNeed <-  as.data.frame(progresobj[14] )
    Transit <-  as.data.frame(progresobj[15] )
    WorkExperience <-  as.data.frame(progresobj[16]) 
    
    
    ## This chunk is to rework variables so that we aggregate modalities with low frequencies together
    ## Categorise main Nationality 
    Individual <- Individual |>
      dplyr::mutate(CountryOfOriginCat = forcats::fct_lump_prop(CountryOfOrigin, prop = .1))
    ## Legal Status 
    # table(Individual$LegalStatus, useNA = "ifany" )
    Individual <- Individual |>
    # Lump together factor levels into "other" if less than 10% of frequency
      dplyr::mutate(LegalStatusCat = forcats::fct_lump_prop(LegalStatus, prop = .1))
    #table(Individual$LegalStatusCat, useNA = "ifany" ) 
    
    ## Legal Status combined with registration reason
    Individual <- Individual |>
      # Lump together factor levels into "other" if less than 10% of frequency
      dplyr::mutate(
        LegalStatusCont =   paste0(LegalStatus,
                                   dplyr::if_else( is.na(RefugeeStatusCategory),
                                            paste0(""),
                                            paste0("-", RefugeeStatusCategory)),
                                   dplyr::if_else( is.na(RegistrationReason),
                                            paste0(""),
                                            paste0("-", RegistrationReason)) ),
        LegalStatusCat2 = forcats::fct_lump_prop( LegalStatusCont, prop = .01))
    #table(Individual$LegalStatusCont, useNA = "ifany" ) 
    #table(Individual$LegalStatusCat2, useNA = "ifany" ) 
    
    
    ## Marrital Status 
    #levels(as.factor(Individual$MaritalStatus))
    #table(Individual$MaritalStatus , useNA = "ifany" )
    Individual <- Individual |>
      dplyr::mutate(MaritalStatusCat = dplyr::case_when(
        MaritalStatus == "Common Law Married" ~ "Married-Engaged",
        MaritalStatus == "Married" ~ "Married-Engaged",
        MaritalStatus == "Engaged" ~ "Married-Engaged",
        MaritalStatus == "Partnership" ~ "Married-Engaged",
        MaritalStatus == "Single" & Age >= 18 ~ "Single_Adult",
        MaritalStatus == "Single"& Age < 18 ~ "Single_Minor",
        MaritalStatus == "Separated" ~ "Divorced-Separated-Widow",
        MaritalStatus == "Divorced" ~ "Divorced-Separated-Widow",
        MaritalStatus == "Widowed" ~ "Divorced-Separated-Widow",
        MaritalStatus == "Unknown" ~ "Unknown",
        is.na(MaritalStatus)  ~ "Unknown" )) 
    
    # table(Individual$MaritalStatusCat , useNA = "ifany" )
    # View(Individual[is.na(Individual$MaritalStatusCat) , c("MaritalStatus", "MaritalStatusCat")] )
    
    ## Linsk in Group
    #levels(as.factor(Individual$RelationshipToFP  ))
    #table(Individual$RelationshipToFP , useNA = "ifany" )
    Individual <- Individual |>
      dplyr::mutate(RelationshipToFPCat = forcats::fct_lump_prop( RelationshipToFP, prop = .005)) 
    
    #table(Individual$RelationshipToFPCat , useNA = "ifany" )
    #View(Individual[is.na(Individual$RelationshipToFPCat) , c("RelationshipToFPCat", "RelationshipToFP")] )
    
    Individual <- Individual |>
      dplyr::mutate(RelationshipToFPCat2 = dplyr::case_when(
        RelationshipToFP == "Focal Point" ~ "Focal Point", 
        RelationshipToFP == "Husband" ~ "Partner", 
        RelationshipToFP == "Wife" ~ "Partner", 
        RelationshipToFP == "Partner (Female)" ~ "Partner", 
        RelationshipToFP == "Partner (Male)" ~ "Partner", 
        RelationshipToFP == "Common Law Husband" ~ "Partner", 
        RelationshipToFP == "Common Law Wife" ~ "Partner", 
        
        RelationshipToFP == "Son" ~ "Family Line", 
        RelationshipToFP == "Daughter" ~ "Family Line", 
        RelationshipToFP == "Grandfather" ~ "Family Line", 
        RelationshipToFP == "Grandmother" ~ "Family Line", 
        RelationshipToFP == "Grandson" ~ "Family Line", 
        RelationshipToFP == "Granddaughter" ~ "Family Line", 
        RelationshipToFP == "Mother" ~ "Family Line", 
        RelationshipToFP == "Father" ~ "Family Line", 
        
        RelationshipToFP == "Aunt" ~ "Extended",  
        RelationshipToFP == "Uncle" ~ "Extended", 
        RelationshipToFP == "Brother" ~ "Extended", 
        RelationshipToFP == "Sister" ~ "Extended", 
        RelationshipToFP == "Cousin (female)" ~ "Extended", 
        RelationshipToFP == "Cousin (male)" ~ "Extended", 
        RelationshipToFP == "Ex-husband" ~ "Extended", 
        RelationshipToFP == "Foster daughter" ~ "Extended", 
        RelationshipToFP == "Foster father" ~ "Extended", 
        RelationshipToFP == "Foster mother" ~ "Extended", 
        RelationshipToFP == "Foster son" ~ "Extended", 
        RelationshipToFP == "Half-brother" ~ "Extended", 
        RelationshipToFP == "Half-sister" ~ "Extended",  
        RelationshipToFP == "Nephew" ~ "Extended", 
        RelationshipToFP == "Niece" ~ "Extended", 
        RelationshipToFP == "Other blood relation (female)" ~ "Extended", 
        RelationshipToFP == "Other blood relation (male)" ~ "Extended",
        
        
        RelationshipToFP == "In Law - Brother" ~ "Extended", 
        RelationshipToFP == "In Law - Sister" ~ "Extended", 
        RelationshipToFP == "In-Law - Daughter" ~ "Extended", 
        RelationshipToFP == "In-Law - Father" ~ "Extended", 
        RelationshipToFP == "In-Law - Mother" ~ "Extended", 
        RelationshipToFP == "In-Law - Son" ~ "Extended", 
        RelationshipToFP == "In-Law (female)" ~ "Extended", 
        RelationshipToFP == "In-Law (male)" ~ "Extended",
        
        RelationshipToFP == "Step-brother" ~ "Extended", 
        RelationshipToFP == "Step-daughter"  ~ "Extended", 
        RelationshipToFP == "Step-father" ~ "Extended", 
        RelationshipToFP == "Step-mother" ~ "Extended", 
        RelationshipToFP == "Step-sister" ~ "Extended", 
        RelationshipToFP == "Step-son" ~ "Extended", 
        
        RelationshipToFP == "No blood relation (female)" ~ "Other", 
        RelationshipToFP == "No blood relation (male)" ~ "Other", 
        RelationshipToFP == "Not specified/unknown (female)" ~ "Other", 
        RelationshipToFP == "Not specified/unknown (male)" ~ "Other", 
        is.na(RelationshipToFP)  ~ "Other" )) 
    #table(Individual$RelationshipToFPCat2 , useNA = "ifany" ) 
    
    ## year of arrival - grouping together pre-2017
    Individual <- Individual |>
      dplyr::mutate( ArrivalYear = lubridate::year(lubridate::as_date(ArrivalDate)),
                     ArrivalYear2 = cut(ArrivalYear, 
                                        breaks = c(0,2017,2018,2019,2020,2021,2022),
                                        labels = c("Arrived in 2017 and before",
                                                   "Arrived in 2018",
                                                   "Arrived in 2019", 
                                                   "Arrived in 2020", 
                                                   "Arrived in 2021",
                                                   "Arrived in 2022"))) 
    
    #table(Individual$ArrivalYear , useNA = "ifany" )
    #table(Individual$ArrivalYear2 , useNA = "ifany" )
 
    ## Adjust Education Level ########
    Individual <- Individual |>
      dplyr::left_join(Education |>
                         dplyr::mutate(ModifiedOnEd = ModifiedOn) |>
                         dplyr::select(IndividualID, Level, Ranking,ModifiedOnEd) ,
                       by = c("IndividualID")) |> 
      dplyr::arrange(desc(ModifiedOnEd)) |> 
      dplyr::filter(!duplicated(IndividualID, fromLast = FALSE)) |> 
      dplyr::mutate(EducationLevelCat = dplyr::case_when(
        Level == "Informal education" ~ "Other",
        Level == "Technical or vocational" ~ "Other",
        Level == "No education" ~ "Up to Grade 5",
        Level == "Kindergarten" ~ "Up to Grade 5",
        Level == "1 year (or Grade 1)" ~ "Up to Grade 5",
        Level == "2 years (or Grade 2)" ~ "Up to Grade 5",
        Level == "3 years (or Grade 3)" ~ "Up to Grade 5",
        Level == "4 years (or Grade 4)" ~ "Up to Grade 5",
        Level == "5 years (or Grade 5)" ~ "Up to Grade 5",
        Level == "6 years (or Grade 6)" ~ "Grade 6-8",
        Level == "7 years (or Grade 7)" ~ "Grade 6-8",
        Level == "8 years (or Grade 8)" ~ "Grade 6-8",
        Level == "9 years (or Grade 9)" ~ "Grade 9-11",
        Level == "10 years (or Grade 10)" ~ "Grade 9-11",
        Level == "11 years (or Grade 11)" ~ "Grade 9-11",
        Level == "12 years (or Grade 12)" ~ "Grade 12-14",
        Level == "13 years (or Grade 13)" ~ "Grade 12-14",
        Level == "14 years (or Grade 14)" ~ "Grade 12-14",
        Level == "University level" ~ "Higher Education",
        Level == "Post university level" ~ "Higher Education",
        Level == "Unknown" ~ "Unknown",
        is.na(Level) ~ "Unknown"))  |>    
    
    #table(Individual$EducationLevelCat, useNA = "ifany")
    # SE.PRE.ENRR School enrollment, preprimary (% gross)
    # SE.PRM.ENRR School enrollment, primary (% gross)
    # SE.SEC.ENRR School enrollment, secondary (% gross)
    # SE.TER.ENRR School enrollment, tertiary (% gross)
    
    # Individual <- Individual |>
    # 
    #   dplyr::left_join(Education |>
    #                      dplyr::mutate(ModifiedOnEd = ModifiedOn) |>
    #                      dplyr::select(IndividualID, Level, Ranking,ModifiedOnEd) ,
    #                    by = c("IndividualID")) |> 
    #   dplyr::arrange(desc(ModifiedOnEd)) |> 
    #   dplyr::filter(!duplicated(IndividualID, fromLast = FALSE)) |>   
      # Education Enroll Level #####
      dplyr::mutate(EducationEnroll = dplyr::case_when(
         Level == "Kindergarten" ~ "is.in.preprimary",
         Level %in% c(  "1 year (or Grade 1)",
                                  "2 years (or Grade 2)",
                                  "3 years (or Grade 3)",
                                  "4 years (or Grade 4)", 
                                  "5 years (or Grade 5)") ~ "is.in.primary",
         Level %in% c( "6 years (or Grade 6)",
                                 "7 years (or Grade 7)" ,
                                 "8 years (or Grade 8)",
                                 "9 years (or Grade 9)",
                                 "10 years (or Grade 10)",
                                 "11 years (or Grade 11)",
                                 "12 years (or Grade 12)",
                                 "13 years (or Grade 13)",
                                 "14 years (or Grade 14)") ~ "is.in.secondary",
         Level %in% c( "University level",
                                 "Post university level") ~ "is.in.tertiary" ))  |>
      
      # EducationEnroll Should #####    
      dplyr::mutate(EducationEnrollShould = dplyr::case_when(
        Age >=3 & Age <6   ~ "should.be.in.preprimary",
        Age >=6 &   Age <11    ~ "should.be.in.primary",
        Age >=11 &   Age <20    ~ "should.be.in.secondary",
        Age >=20 &   Age < 24   ~ "should.be.in.tertiary" )) |>
      
      # Education Enroll atRightAge #####  
      dplyr::mutate(EducationEnrollatRightAge = dplyr::case_when(
        Age >=3 & Age <6 & 
          Level == "Kindergarten" ~ "yes",
        Age >=6 &   Age <11  & 
          Level %in% c(  "1 year (or Grade 1)",
                                "2 years (or Grade 2)",
                                "3 years (or Grade 3)",
                                "4 years (or Grade 4)", 
                                "5 years (or Grade 5)") ~ "yes",
        Age >=11 &   Age <20  & 
          Level %in% c( "6 years (or Grade 6)",
                                "7 years (or Grade 7)" ,
                                "8 years (or Grade 8)",
                                "9 years (or Grade 9)",
                                "10 years (or Grade 10)",
                                 "11 years (or Grade 11)",
                                 "12 years (or Grade 12)",
                                 "13 years (or Grade 13)",
                                 "14 years (or Grade 14)") ~ "yes",
        Age >=20 &   Age < 24 & 
          Level %in% c( "University level",
                                 "Post university level") ~ "yes" ))  |>
      
      dplyr::mutate(EducationEnrollatRightAge = dplyr::if_else(
        is.na(EducationEnrollatRightAge) ,paste0("no"),  EducationEnrollatRightAge )) |>
    
    # View(Individual[ !(is.na(Individual$EducationEnrollShould)) ,
    #                  c("Age",  "EducationEnroll", 
    #                     "EducationEnrollShould", 
    #                     "EducationEnrollatRightAge"#, 
    #                     # "EducationEnrollGross", 
    #                     #"EducationEnrollNet"
    #                    )])
    # 
    # table(Individual$EducationEnroll , useNA = "ifany")
    # table(Individual$EducationEnrollatRightAge , useNA = "ifany")
    # table(Individual$EducationEnrollShould, useNA = "ifany")
    # table(Individual$EducationEnrollatRightAge, Individual$EducationEnrollShould, useNA = "ifany")
    # table(Individual$EducationEnroll, Individual$EducationEnrollShould, useNA = "ifany")
    
    # SE.PRM.CUAT.ZS Educational attainment, at least completed primary, population 25+ years, total (%) (cumulative)
    # SE.SEC.CUAT.LO.ZS Educational attainment, at least completed lower secondary, population 25+, total (%) (cumulative)
    # SE.SEC.CUAT.UP.ZS Educational attainment, at least completed upper secondary, population 25+, total (%) (cumulative)
    # SE.SEC.CUAT.PO.ZS Educational attainment, at least completed post-secondary, population 25+, total (%) (cumulative) 
    # SE.TER.CUAT.DO.ZS Educational attainment, Doctoral or equivalent, population 25+, total(%) (cumulative)
    
    # SE.TER.CUAT.ST.ZS Educational attainment, at least completed short-cycle tertiary, population 25+,total (%) (cumulative)
    # SE.TER.CUAT.BA.ZS Educational attainment, at least Bachelor's or equivalent, population 25+, total (%) (cumulative)
    # SE.TER.CUAT.MS.ZS Educational attainment, at least Master's or equivalent, population 25+, total (%) (cumulative)
    #Individual <- Individual |>
      dplyr::mutate(EducationAttainment = dplyr::case_when(
        Level == "Informal education" ~ "Not Measured",
        Level == "Technical or vocational" ~ "Not Measured",
        Level == "No education" ~ "Not Measured",
        Level == "Kindergarten" ~ "Not Measured",
        Level == "1 year (or Grade 1)" ~ "PRM",
        Level == "2 years (or Grade 2)" ~ "PRM",
        Level == "3 years (or Grade 3)" ~ "PRM",
        Level == "4 years (or Grade 4)" ~ "PRM",
        Level == "5 years (or Grade 5)" ~ "PRM",  
        Level == "6 years (or Grade 6)" ~ "SEC.LO",
        Level == "7 years (or Grade 7)" ~ "SEC.LO",
        Level == "8 years (or Grade 8)" ~ "SEC.LO",
        Level == "9 years (or Grade 9)" ~ "SEC.LO",
        Level == "10 years (or Grade 10)" ~ "SEC.UP",
        Level == "11 years (or Grade 11)" ~ "SEC.UP",
        Level == "12 years (or Grade 12)" ~ "SEC.UP",
        Level == "13 years (or Grade 13)" ~ "SEC.UP",
        Level == "14 years (or Grade 14)" ~ "SEC.UP",
        Level == "University level" ~ "SEC.PO",
        Level == "Post university level" ~ "TER.DO",
        Level == "Unknown" ~ "Not Measured",
        is.na(Level) ~ "Not Measured")) 
    #table(Individual$EducationAttainment, useNA = "ifany")
    
    Individual<- Individual |>
      dplyr::mutate(EducationAttainment = dplyr::if_else( Age <25,
                                                          "Not Applicable",
                                                          EducationAttainment ))
    
    # table(Individual$EducationAttainment, useNA = "ifany")

 
## Occupation - https://ilostat.ilo.org/resources/concepts-and-definitions/description-employment-by-occupation/ 
## EMP_TEMP_SEX_OC2_NB_A -->  ILOSTAt

  ## Isco code to analyse workexperience
  # isco <- readr::read_csv(paste0(mainDirroot,"/data-raw/isco.csv")) 
  isco <- readxl::read_excel( system.file("isco.xlsx", package = "proGresAnalysis") , sheet = "isco") |>
    dplyr::select( - isco_parent2, - isco_parent_name2, 
                    - isco_parent3, - isco_parent_name3, 
                    - level1dup, - level2dup, - level3dup )
# names(isco)

Individual <- Individual |> 
  dplyr::left_join(WorkExperience |>
                     dplyr::mutate(WorkExperienceAsy = WorkType) |>
                     dplyr::mutate(ModifiedOnWorkAsy = ModifiedOn)  |> 
                     dplyr::filter(CountryOfWork == ctr ) |> 
                     dplyr::arrange(desc(ModifiedOnWorkAsy)) |> 
                     dplyr::filter(!duplicated(IndividualID, fromLast = FALSE)) |>
                     dplyr::select(IndividualID, WorkExperienceAsy, 
                                   #CountryOfWork,
                                   ModifiedOnWorkAsy),
                   by = c("IndividualID")) |> 
  dplyr::left_join(WorkExperience |>
                     dplyr::mutate(WorkExperience = WorkType) |>
                     dplyr::mutate(ModifiedOnWork = ModifiedOn)  |> 
                     dplyr::filter(CountryOfWork != ctr ) |> 
                     dplyr::arrange(desc(ModifiedOnWork)) |> 
                     dplyr::filter(!duplicated(IndividualID, fromLast = FALSE)) |>
                     dplyr::select(IndividualID, 
                                   WorkExperience, 
                                   CountryOfWork,
                                   ModifiedOnWork),
                   by = c("IndividualID"))   |> 

#Individual <- Individual |> 
  dplyr::left_join(isco, 
                    by = c("WorkExperience" = "isco_name"))  |> 
  dplyr::left_join(isco, 
                    by = c("WorkExperienceAsy" = "isco_name"))  |> 
  dplyr::mutate( Lskill = max(LSkill.x, LSkill.y),
                 isei = max(isei.x,isei.y),
                 siops = max(siops.x, siops.y),
                 isco_parent1 = max(isco_parent1.x, isco_parent1.y) )


 ## Specific Needs ########################
SpecificNeed <- SpecificNeed |> 
  dplyr::mutate( SpecificNeedSub = paste0( SPNCategory,
                                  if_else( is.na(`SPNSub.Category`),
                                           paste0(""),
                                           paste0("- ", `SPNSub.Category`))))

 ## Filter Assistance type ################
Assistance <-  Assistance |>
  dplyr::mutate( AssistanceSub = paste0( AssistanceType,
                                          dplyr::if_else( is.na(`AssistanceSub.Type`),
                                                          paste0(""),
                                                          paste0("-", `AssistanceSub.Type`)),
                                          dplyr::if_else( is.na(`AssistanceSub.Sub.Type`),
                                                                   paste0(""),
                                                                   paste0("- ", `AssistanceSub.Sub.Type`)) ))|>
  dplyr::mutate( AssistanceCash =  dplyr::if_else( stringr::str_detect(AssistanceSub,  "cash" ),
                                                          TRUE,
                                                          FALSE))  |>
  dplyr::mutate( AssistanceCash =  dplyr::if_else( stringr::str_detect(AssistanceSub,   "Cash") ,
                                                    TRUE,
                                                    FALSE))  |>
  dplyr::mutate( AssistanceWASH =  dplyr::if_else( stringr::str_detect(AssistanceSub,  "WASH" ),
                                                    TRUE,
                                                    FALSE))  |>
  dplyr::mutate( AssistanceShelter =  dplyr::if_else( stringr::str_detect(AssistanceSub,   "Shelter") ,
                                                    TRUE,
                                                    FALSE))   |> 
 dplyr::mutate( AssistanceYear = lubridate::year(lubridate::as_date(ActualStartDate))  )
 

# table(Asstype$AssistanceSub, useNA = "ifany")
# table(Asstype$AssistanceCash, useNA = "ifany")
# table(Asstype$AssistanceWASH, useNA = "ifany")
# table(Asstype$AssistanceShelter, useNA = "ifany")
# levels(as.factor(Assistance$AssistanceType))

#  aggregateAtCaseLevel ####################

## variables are then aggregated to Registration Case level which is the main unit of analysis
## Aggregate key information at case level #####
RegistrationGroupall <- RegistrationGroup |> 
  
  
  ## Add gender, age group of representative #######
  dplyr::left_join(Individual |> 
                   dplyr::filter(RelationshipToFP == "Focal Point")   |>
                   dplyr::select(RegistrationGroupID, Age, Sex) |>
                   dplyr::mutate( AgeFP = Age,
                                  SexFP = Sex) |>
                   dplyr::select(-Age, -Sex)    , # |>
                 by = c("RegistrationGroupID")) |>
  
  dplyr::filter(!(is.na(SexFP)) ) |>
  ## Case when there's no Focal Point
  # #   table(RegistrationGroupall$SexFP, useNA = "ifany")
  # View( Individual |>
  #         dplyr::inner_join(RegistrationGroupall |>
  #                            dplyr::filter(is.na(SexFP))|>
  #                          dplyr::select(RegistrationGroupID),                          , 
  #                          by = c("RegistrationGroupID")) )
  
  
  ##  WorkExperience skill level #######
# dplyr::left_join(Individual |> 
#                    dplyr::group_by( RegistrationGroupID ) |>
#                    dplyr::summarise ( 
#                      EducRankMax = max(Ranking),
#                      OccupMaxSkill = max(Lskill),
#                      OccupMaxisei = max(isei),
#                      OccupMaxsiops = max(siops),
#                      OccupMaxisco_parent1 = max(isco_parent1)
#                    ),
#                  by = c("RegistrationGroupID")) |>
  
  
  ## Case Size #####
  dplyr::mutate(GroupSize1 = cut(GroupSize, 
                               breaks = c(0,1,2,3,4,5, 60),
                               labels = c("Size1", "Size2", "Size3",
                                          "Size4", "Size5", "Size6+"))) |>
  
  
  ## Add HH Ratio Dependency, , average & standard deviation age ..  ####
  dplyr::left_join(Individual |> 
                   dplyr::group_by( RegistrationGroupID    ) |>
                   dplyr::summarise ( totalInd = dplyr::n(),
                                      totalF =  sum(Sex == "Female"),
                                      totalWorkingAge =  sum(Age >=15 & Age < 60),
                                      totalYouth =  sum(Age <15  ),
                                      totalEldern =  sum(Age > 60) ,
                                      ageAvg = mean(Age),
                                      ageSd = sd(Age) ),
                 by = c("RegistrationGroupID")) |>
  
  ## Remove records with no match case t Ind
  dplyr::filter(!(is.na(totalInd))) |>
  
  ## Discretise Average & SD for age
  # table(RegistrationGroupall$ageAvg, useNA= "ifany") hist(RegistrationGroupall$ageAvg)
  dplyr::mutate(ageAvgCat = dplyr::case_when(
    ageAvg <= 18   ~ "below.18", 
    ageAvg > 18 & ageAvg <= 35  ~ "between.19.35",
    ageAvg > 35 & ageAvg <= 59  ~ "between.36.59",
    ageAvg > 59 ~ "over.60")) |>
  dplyr::mutate(ageAvgCat = factor(ageAvgCat, 
                                   levels = c("below.18", "between.19.35", "between.36.59", 
                                              "over.60"))) |>
  # table(RegistrationGroupall$ageAvgCat, useNA= "ifany")
  
  # table(RegistrationGroupall$ageSd, useNA= "ifany") hist(RegistrationGroupall$ageSd)
  dplyr::mutate(ageSdCat = dplyr::case_when(
    is.na(ageSd) ~ "unique",  
    ageSd <= 5   ~ "below.5",  
    ageSd > 5 & ageSd <= 10  ~ "between.6.10",
    ageSd > 10 & ageSd <= 20  ~ "between.11.20",
    ageSd > 20 ~ "over.21")) |>
  dplyr::mutate(ageSdCat = factor(ageSdCat, 
                                  levels = c("unique","below.5", "between.6.10", "between.11.20", 
                                             "over.21"))) |>
  # table(RegistrationGroupall$ageSdCat, useNA= "ifany")
  
  #table(RegistrationGroupall$ratio_f, useNA= "ifany") hist(RegistrationGroupall$ratio_f)
  dplyr::mutate ( ratioFemale = totalF/ totalInd ) |>
  dplyr::mutate(ratioFemaleCat = dplyr::case_when(
    ratioFemale == 0 ~ "no.female", 
    ratioFemale > 0 & ratioFemale < 0.5  ~ "few.female",
    ratioFemale == 0.5 ~ "half.female",
    ratioFemale > 0.5 & ratioFemale < 1  ~ "majority.female",
    ratioFemale == 1 ~ "all.female")) |>
  dplyr::mutate(ratioFemaleCat = factor(ratioFemaleCat, 
                                        levels = c("no.female", "few.female", "half.female", 
                                                   "majority.female", "all.female"))) |>
  
  dplyr::mutate ( ratioDependant = totalWorkingAge / totalInd ) |>
  dplyr::mutate(ratioDependantCat = dplyr::case_when(
    ratioDependant == 0 ~ "all.dependant", 
    ratioDependant > 0 & ratioDependant < 0.5  ~ "few.dependant",
    ratioDependant == 0.5 ~ "half.dependant",
    ratioDependant > 0.5 & ratioDependant < 1  ~ "majority.dependant",
    ratioDependant == 1 ~ "no.dependant")) |>
  dplyr::mutate(ratioDependantCat = factor(ratioDependantCat, 
                                           levels = c("no.dependant", "few.dependant", "half.dependant",
                                                      "majority.dependant", "all.dependant"))) |>
  
  # table(RegistrationGroupall$ratioDependantCat, useNA= "ifany")
  # View(RegistrationGroupall[ is.na(RegistrationGroupall$ratioDependantCat), ])
  
  dplyr::mutate ( ratioYouth = totalYouth/ totalInd ) |>
  dplyr::mutate(ratioYouthCat = dplyr::case_when(
    ratioYouth == 0 ~ "no.youth", 
    ratioYouth > 0 & ratioYouth < 0.5  ~ "few.youth",
    ratioYouth == 0.5 ~ "half.youth",
    ratioYouth > 0.5 & ratioYouth < 1  ~ "majority.youth",
    ratioYouth == 1 ~ "all.youth")) |>
  dplyr::mutate(ratioYouthCat = factor(ratioYouthCat, 
                                       levels = c("no.youth", "few.youth", "half.youth", 
                                                  "majority.youth", "all.youth"))) |>
  
  
  dplyr::mutate ( ratioEldern = totalEldern/ totalInd ) |>
  dplyr::mutate(ratioEldernCat = dplyr::case_when(
    ratioEldern == 0 ~ "no.eldern", 
    ratioEldern > 0 & ratioEldern < 0.5  ~ "few.eldern",
    ratioEldern == 0.5 ~ "half.eldern",
    ratioEldern > 0.5 & ratioEldern < 1  ~ "majority.eldern",
    ratioEldern == 1 ~ "all.eldern")) |>
  dplyr::mutate(ratioEldernCat = factor(ratioEldernCat, 
                                        levels = c("no.eldern", "few.eldern", "half.eldern", 
                                                   "majority.eldern", "all.eldern"))) |>
  
  
  
  dplyr::select ( - ratioEldern)  |>
  dplyr::select ( - ratioYouth)  |>
  dplyr::select ( - ratioDependant)  |>
  dplyr::select ( - ageAvg)  |>
  dplyr::select ( - ageSd)  |>
  
  
  ## Add marital Status #######
  dplyr::left_join(Individual |> 
                   tidyr::pivot_wider(id_cols = c("RegistrationGroupID") ,
                                      names_from = MaritalStatusCat,
                                      values_from = "IndividualID",
                                      values_fn =  length ),
                 by = c("RegistrationGroupID")) |>
  
  
  ## Add aggregated spNeeds  #######
  dplyr::left_join(SpecificNeed |> 
                   dplyr::left_join( y = Individual,
                                     by = c("IndividualID") ) |> 
                   dplyr::group_by( RegistrationGroupID, SPNCategory   ) |> 
                   dplyr::summarise(n = dplyr::n())  |> 
                   dplyr::filter( ! (is.na(RegistrationGroupID) ))  |>
                   tidyr::pivot_wider(names_from  = SPNCategory,
                                      values_from = n) ,
                 by = c("RegistrationGroupID")) |>
  
  
  ## Add count of needs within Case
  dplyr::left_join(SpecificNeed |> 
                     dplyr::left_join( y = Individual,
                                       by = c("IndividualID") ) |> 
                     dplyr::group_by( RegistrationGroupID   ) |> 
                     dplyr::summarise(countneed = dplyr::n()),
                   by = c("RegistrationGroupID")) |>
  
  ## Add Assistance Records #######
  dplyr::left_join(Assistance |> 
                   # filter( AssistanceYear == 2020) |> 
                   dplyr::left_join( y = Individual,
                                     by = c("IndividualID", "RegistrationGroupID") ) |> 
                   dplyr::group_by( RegistrationGroupID, AssistanceCash   ) |> 
                   dplyr::summarise(n = dplyr::n()) |> 
                   filter( ! (is.na(RegistrationGroupID) ))  |>
                   tidyr::pivot_wider(names_from  = AssistanceCash,
                                      names_glue = "{AssistanceCash}_{.value}",
                                      values_from = n) |>
                   dplyr:: mutate( AssistanceCash =  dplyr::case_when(
                     TRUE_n >= 0  & is.na(FALSE_n) ~ "All.case.get.cash",
                     TRUE_n >= 0  & FALSE_n >= 0 ~ "Some.members.get.cash",
                     is.na(TRUE_n) ~ "No.cash"))  |>
                   dplyr::select ( - TRUE_n)  |>
                   dplyr::select ( - FALSE_n)  ,
                 by = c("RegistrationGroupID")) |> 
 
    dplyr:: mutate( AssistanceCash2 =  dplyr::if_else( is.na(AssistanceCash),
                                                     "No.cash",
                                                     AssistanceCash))  |>
    dplyr:: mutate( AssistanceCashBol =  dplyr::if_else( AssistanceCash2 == "No.cash",
                                                       FALSE,TRUE
                                                        )) |> 
    dplyr:: mutate( GotAssistance =  dplyr::if_else( is.na(AssistanceCash),
                                                   FALSE,TRUE
                                                        )) |>
    dplyr::select ( - AssistanceCash) |>   
  
  # dplyr::left_join(Assistance |> 
  #                    # filter( AssistanceYear == 2020) |> 
  #                    dplyr::left_join( y = Individual) |> 
  #                    dplyr::group_by( RegistrationGroupID, AssistanceSub   ) |> 
  #                    dplyr::summarise(n = dplyr::n()) |> 
  #                    filter( ! (is.na(RegistrationGroupID) ))  |>
  #                    tidyr::pivot_wider(names_from  = AssistanceSub,
  #                                       values_from = n)    )  |> 
  
  #RegistrationGroupall1 <- RegistrationGroupall  |> 
# 
#   library(dplyr)
# library(tidyr)
# df |> mutate(val=1) |> 
#   pivot_wider(names_from = country,
#               values_from = val) |> 
#   mutate(across(-RegistrationGroupID, ~replace_na(.x, 0))) |>
#   mutate(across(-RegistrationGroupID, ~ifelse(.x==1, TRUE,FALSE)))

## Clean  that fame... ######
## Replace NA by 0 
  dplyr::select ( - OwningOffice)  |>
  dplyr::select ( - WillingToReturn)  |>
  dplyr::select ( - BusinessUnit)  |>
  dplyr::filter(!(is.na(GroupSize1))) |> 

    
    
  ## Some records have missing age info preventing ratio to be calculated
  # table(RegistrationGroupall$ageAvgCat, useNA = "ifany")
  # View(RegistrationGroupall[ is.na(RegistrationGroupall$ageAvgCat), ])
  dplyr::filter(!(is.na(ageAvgCat)))  |>
  dplyr::mutate( dplyr::across(where(is.integer), ~ tidyr::replace_na(.x, 0)) ) |>
#  dplyr::mutate( dplyr::across(dplyr::everything(), ~ tidyr::replace_na(.x, 0)) ) |>
#  replace(is.na(), 0) #|>
#RegistrationGroupall1 <- RegistrationGroupall |> 
  #  dplyr::mutate(dplyr::across(everything(), ~ replace_na(.x, 0))) |>
  dplyr::mutate(dplyr::across( where(is.integer), ~ dplyr::if_else( .x > 0 , TRUE,FALSE) ) ) |>
  
  ## Clean variable name
  janitor::clean_names()
  


## Filter popdata for the country report
popdatactr <-   popdata::pd_asr("demographics", year = 2021)  %>% 
  as.data.frame() %>% 
  #mutate( total = as.integer(total))  %>%
  dplyr::left_join( y= unhcrdatapackage::reference, 
                    by = c("asylum" = "UNHCRcode"))  %>%
  dplyr::filter(ctryname  == ctr ) %>%
  dplyr::select(ctryname , populationType, total) %>%
  dplyr::group_by( ctryname, populationType  ) %>%
  dplyr::summarise(totalasr = sum( total) )  %>%
  mutate(LegalStatus = case_when(
                 populationType == "ASY" ~ "Asylum Seeker",
                 populationType == "HST" ~ "Not of concern", 
                 populationType == "IDP" ~ "Internally displaced person",
                 populationType == "OOC" ~ "Other of concern",
                 populationType == "RDP" ~ "Returned IDP",
                 populationType == "REF" ~ "Refugee",
                 populationType == "RET" ~ "Returnee",
                 populationType == "ROC" ~ "???",
                 populationType == "STA" ~ "Stateless (non-refugee)",
                 populationType == "VDA" ~ "Other of concern")) %>%
  dplyr::select(LegalStatus, totalasr)  %>%
  dplyr::group_by( LegalStatus ) %>%
  dplyr::summarise(totalasr = sum( totalasr) ) 

 #require(wbstats)
 wb_data <- wbstats::wb_data(
  indicator = c( "SE.PRM.CUAT.ZS", # Educational attainment, at least completed primary, population 25+ years, total (%) (cumulative)
                 "SE.SEC.CUAT.LO.ZS", # Educational attainment, at least completed lower secondary, population 25+, total (%) (cumulative)
                 "SE.SEC.CUAT.UP.ZS", # Educational attainment, at least completed upper secondary, population 25+, total (%) (cumulative)
                 "SE.SEC.CUAT.PO.ZS", # Educational attainment, at least completed post-secondary, population 25+, total (%) (cumulative) 
                 "SE.TER.CUAT.DO.ZS",  # Educational attainment, Doctoral or equivalent, population 25+, total(%) (cumulative)
                 "SE.TER.CUAT.ST.ZS", # Educational attainment, at least completed short-cycle tertiary, population 25+,total (%) (cumulative)
                 "SE.TER.CUAT.BA.ZS", # Educational attainment, at least Bachelor's or equivalent, population 25+, total (%) (cumulative)
                 "SE.TER.CUAT.MS.ZS", # Educational attainment, at least Master's or equivalent, population 25+, total (%) (cumulative)  
                 "SE.PRE.ENRR", # School enrollment, preprimary (% gross)
                 "SE.PRM.ENRR", # School enrollment, primary (% gross)
                 "SE.SEC.ENRR", # School enrollment, secondary (% gross)
                 "SE.TER.ENRR" # School enrollment, tertiary (% gross)
                   ),
  #start_date = "2010",
  mrv = 1,
  country = ctr,
  return_wide = FALSE) |>
  dplyr::select( indicator_id, indicator, date, value ) |>
  dplyr::mutate( source = "UNESCO Institute for Statistics")

  
  progres <- list(Individual, #[1]  
                  RegistrationGroup, #[2] 
                  Assistance , #[3] 
                  Document , #[4] 
                  Education , #[5] 
                  EntitlementCard , #[6] 
                  IndividualProperty , #[7] 
                  Language , #[8] 
                  Nationality , #[9] 
                  Relative , #[10] 
                  Representative , #[11] 
                  Skill , #[12] 
                  SocioEconomic , #[13] 
                  SpecificNeed , #[14] 
                  Transit , #[15] 
                  WorkExperience,  #[16]
                  RegistrationGroupall, #[17]
                  popdatactr, #[18] 
                  wb_data) #[19]
  return(progres)
    
    
  }
```

```{r examples-data_recode }
progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,
                       ctr = "Ecuador")

```

```{r tests-data_recode}

```


#  5 High Level Key Questions

 * __Reach-out__: What are the main profile of people registering with UNHCR
 
 * __Inclusion__: What could be main obstacles to inclusion in host country for those who registered?
 
 * __Protection__: What are the main Protection Risks and Needs among those registered?

 * __Segmentation__: What are the main homogeneous statistical profiles among those registered?

 * __Assistance__: What Responses are being provided and to Whom?



## Chapter 1: Profile of people registering with UNHCR

 1. What subset of the total population does it represent?
 
 2. How much the profiles of refugees differs from the population of local population? 
 
 3. How much we know about their Intention?

### 1.1 Registration coverage

```{r function-plot_reach_registration}
#' @title Analytic chart to display registration coverage
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_reach_registration <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) {

   Individual <- as.data.frame(progres[1] ) 
   popdatactr <- as.data.frame(progres[18] ) 
  
    
## get popdata report in order to have comparison by legal status
p <- Individual |> 
  dplyr::group_by( LegalStatus  ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
  filter( ! (is.na(LegalStatus) )) |> 
  mutate(n = as.numeric(n), 
         ValRound =  ifelse(n > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(n)),
                          as.character(n) ) )   |>
  dplyr::left_join( y= popdatactr, 
                    by = c("LegalStatus" = "LegalStatus"))  |> 
  mutate(notregistered =  as.integer(ifelse(is.na(totalasr), 0, paste(totalasr - n) ))) |> 
  mutate(coverage =  ifelse(is.na(totalasr), 
                        paste0(ValRound, " registered, not published as Stat"),
                        paste0(ValRound, " registered, ", scales::label_number_si(accuracy = 0.1)(n/totalasr *100), 
                               " % of total Stat")) )   |> 
  dplyr::select(LegalStatus, coverage, notregistered, n )  |> 
  tidyr::pivot_longer(
    cols = starts_with("n"), # "LegalStatus", "coverage"
    names_to = "datarecord", 
    values_to = "ind"
  )   |>
  ggplot( aes(x = reorder(LegalStatus, ind),
              y = ind,
              fill = datarecord)) + 
  geom_bar(stat = "identity", 
           position = "stack"
           # fill = "#0072bc"
  ) + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) +
  scale_fill_manual(values = c( "blue", "gray"))+ 
  guides(fill="none") + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, ind < max(ind) / 1.5 &
                                            datarecord =="notregistered"),
              aes(x = reorder(LegalStatus, ind),
                  y = ind,
                  label= coverage),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
             # position = position_stack(vjust= 0.5),
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, ind >= max(ind) / 1.5  &
                                            datarecord =="notregistered" ),
              aes(x = reorder(LegalStatus, ind),
                  y = ind,
                  label= coverage),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
             # position = position_stack(vjust= 0.5),
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +    
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank() ) + 
  labs(title = "What is the share among the total people of concern that is registered with UNHCR?",
       subtitle = paste0("Assessing gap between Annual Statistical Reports (grey) with Active registered Cases (Blue) in " , ctr),   
       x = "",
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl, "compared with extract from Internal Annual Statistical Report from http://popdata.unhcr.org.\n There might be situation where the numbe of registered individual is higher than numbers reported as official statistics. That (grey) excedent will then appear as negative.") )

return(p)

  ## Add annotation -- use ggannotate to get the right  coordinate within chart
  #remotes::install_github("mattcowgill/ggannotate")
  #ggannotate::ggannotate()
  
  # geom_curve(aes(xend = 10.9476141263782, yend = 2959.93589579213, 
  #                x = 6.91965137456717, y = 28668.752697603),
  #            size = 2, color = "tan",
  #            arrow = arrow(length = unit(0.07, "npc"))) +
  # ggtext::geom_textbox(data = data.frame(x = 6.91965137456717, y = 28668.752697603, 
  #                                        label = "Why so many people are using **other** category? \n Is there an important missing category within Primes?"),
  #                     mapping = aes(x = x, y = y, label = label),
  #                     width = unit(0.6, "npc"),
  #                     family = "Lato", size = 7, fill = "cornsilk",
  #                     inherit.aes = FALSE)
 }


```


```{r examples-plot_reach_registration, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_reach_registration (progres = progres , 
                         ctr = "Ecuador", 
                         ridl = "Ecuador",
                                    thisyear = 2021)
```

```{r tests-plot_reach_registration}

```


### 1.2 Age Pyramid

```{r function-plot_reach_agepyr}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_reach_agepyr <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl" ,
                                    thisyear = 2021) { 
#install.packages("idbr")
library("idbr")
#idbr::idb_api_key('Your API key goes here')
idbr::idb_api_key(Sys.getenv("CENSUS"))

#names(Individual)
#table(Individual$Age, useNA= "ifany")

# https://stackoverflow.com/questions/15816073/population-pyramid-w-projection-in-r
# https://stackoverflow.com/questions/14680075/simpler-population-pyramid-in-ggplot2/36804394#36804394
#thisyear <- 2021


Individual <- as.data.frame(progres[1] ) 
pyramid_data <- idbr::get_idb(
  country = ctr,
  year = thisyear,
  age = 0:100,
  sex = c("male", "female"))  |> 
  mutate(Source = "Census") |>
  mutate(Age = age) |>
  mutate(Sex = sex) |>
  dplyr::select(Age, Sex, pop, Source)

pyramid_data1 <- Individual |> 
  filter( ! (is.na(Age) )) |> 
  dplyr::group_by(Age , Sex  ) |> 
  dplyr::summarise(pop= n()) |> 
  filter( ! Sex %in% c("Other","Unknown") )  |> 
  mutate(Source = "Registered") |>
  bind_rows(pyramid_data)|> 
  group_by(Source) |> 
  mutate(popprop = round( pop/sum(pop) *100 , 3))|> 
  filter( Age <= 101 ) 

p<- ggplot(data = pyramid_data1, aes(x = Age, 
                       y = popprop , 
                       fill = Sex)) +
  
  #bars for all but 2030
  geom_bar(data = pyramid_data1 |> 
             filter(Sex == "Female",
                    Source == "Registered" ),
           stat = "identity",
           position = "identity") + 
  
  geom_bar(data = pyramid_data1 |> 
             filter(Sex == "Male", 
                    Source == "Registered" ),
           stat = "identity",
           position = "identity",
           mapping = aes(y = -popprop)) +
  
  #steps for 2030
  geom_step(data =  pyramid_data1 |> 
              filter(Sex == "Female", 
                     Source == "Census"), 
            aes(x = Age ,
                y = popprop  )) +
  
  geom_step(data =  pyramid_data1 |> 
              filter(Sex == "Male", 
                     Source == "Census"), 
            aes(x = Age, 
                y = -popprop)) +
  
  coord_flip() +
  guides(fill="none") + 
  scale_y_continuous(labels = abs) +
  scale_colour_manual(values = c("#126db4","#01ab91"),
                      aesthetics = c("colour", "fill")) +
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.y  = element_line(color = "#cbcbcb"), 
        panel.grid.major.x  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = "How Much Age & Gender of Registered Population Differ from Host Population?",
       subtitle = paste0("Comparing profiles between registered and host population (black lines) in ", ctr),   
       x = "Age Bracket",
       y = "As % of total population",
       caption = paste0("Source: Data available in RIDL @ ", ridl, " compared with baseline demographic profile for the host population - source US Census Bureau ") ) + 
  
    ggtext::geom_textbox(data = data.frame(x = 96, y = -0.52, 
                                           label = "Male"),
                        mapping = aes(x = x, y = y, label = label),
                        width = unit(0.2, "npc"),
                        family = "Lato", size = 5, fill = "#01ab91",
                        inherit.aes = FALSE) +
    ggtext::geom_textbox(data = data.frame(x = 96, y = 0.52, 
                                           label = "Female"),
                        mapping = aes(x = x, y = y, label = label),
                        width = unit(0.2, "npc"),
                        family = "Lato", size = 5, fill = "#126db4",
                        inherit.aes = FALSE)
 return(p) 
  ## Add annotation -- use ggannotate to get the right  coordinate within chart
  #remotes::install_github("mattcowgill/ggannotate")
  #ggannotate::ggannotate()
  
  # geom_curve(aes(xend = 10.9476141263782, yend = 2959.93589579213, 
  #                x = 6.91965137456717, y = 28668.752697603),
  #            size = 2, color = "tan",
  #            arrow = arrow(length = unit(0.07, "npc"))) +
  # ggtext::geom_textbox(data = data.frame(x = 6.91965137456717, y = 28668.752697603, 
  #                                        label = "Why so many people are using **other** category? \n Is there an important missing category within Primes?"),
  #                     mapping = aes(x = x, y = y, label = label),
  #                     width = unit(0.6, "npc"),
  #                     family = "Lato", size = 7, fill = "cornsilk",
  #                     inherit.aes = FALSE)


# : Is it the same as the local population? Does it coincide with the data from the country of origin? If one group, such as adult men or young children, seems under- or over-represented, find out why.

}

```


```{r examples-plot_reach_agepyr, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_reach_agepyr (progres = progres , 
                         ctr = "Ecuador", 
                         ridl = "data-should-be-on-ridl" ,
                         thisyear = 2021)

```

```{r tests-plot_reach_agepyr}

```



### 1.3 Willing To Return

```{r function-plot_reach_return}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_reach_return <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
#names(RegistrationGroup)
#table(RegistrationGroup$WillingToReturn, useNA= "ifany")
  
  
    

    Individual <- as.data.frame(progres[1] ) 
    RegistrationGroup <- as.data.frame(progres[2] )
    
if( nlevels(as.factor(RegistrationGroup$WillingToReturn)) > 0 ) {
p <- RegistrationGroup |> 
  dplyr::mutate( WillingToReturn = dplyr::if_else( is.na(WillingToReturn) ,
                                                   paste0("No info recorded"), 
                                                   WillingToReturn)  ) |>
  dplyr::left_join( y = Individual) |> 
    dplyr::group_by( RegistrationGroupID, WillingToReturn,CountryOfOriginCat   ) |> 
    dplyr::summarise(Origin = dplyr::n())  |> 
   dplyr::filter( ! (is.na(RegistrationGroupID) ))  |>
    tidyr::pivot_wider(names_from  = CountryOfOriginCat,
                       names_glue = "{.value}_{CountryOfOriginCat}",
                       values_from = Origin) |> 
  #replace(is.na(.), 0) |>
  dplyr::mutate( dplyr::across(where(is.integer), ~ tidyr::replace_na(.x, 0)) ) |>
  #  dplyr::mutate(dplyr::across(everything(), ~ replace_na(.x, 0))) |>
  dplyr::mutate(dplyr::across( where(is.integer), ~ dplyr::if_else( .x > 0 , TRUE,FALSE) ) )  |>
 
  tidyr::pivot_longer(
    cols = starts_with("Origin"),
    names_to = "Orig",
    names_prefix = " ",
    values_to = "cases",
    values_drop_na = TRUE ) |> 
  dplyr::filter( cases == "TRUE" ) |>
  
  dplyr::group_by(WillingToReturn, Orig ) |> 
  dplyr::summarise(n = dplyr::n())   |> 
  mutate(n = as.numeric(n), 
         nRound =  ifelse(n > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(n)),
                          as.character(n) ) ) |>  
  ggplot( aes(x = reorder(WillingToReturn,n), 
              y = n )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  facet_grid(. ~ Orig ) +
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, n < max(n) / 1.5),
              aes(x = reorder(WillingToReturn, n),
                  y = n,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  geom_label( data =   function(x) subset(x, n >= max(n) / 1.5),
              aes(x = reorder(WillingToReturn, n),
                  y = n,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = "What are the intentions in terms of return by Country of Origin?",
       subtitle = paste0("Among the ", scales::label_comma()(nrow(RegistrationGroup)),
                         " case records, ",
                         scales::label_comma()(nrow(RegistrationGroup |>dplyr::filter( !(is.na(WillingToReturn) )))),
                         " includes information on this topic in ", ctr),   
       x = "",
       y = " ",
       caption = paste0("Source: Data available in RIDL @ ", ridl, "\n",
                        "Only nationality with a frequency over 10% are included. Note that this information is collected at case level.") )
  
  return(p)
  
} else {
  #cat("There's not a single records of intention within the registration database")
  return( cat("There's not a single records of intention within the registration database"))
}

}
```


```{r examples-plot_reach_return, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_reach_return(progres  = progres , 
                         ctr = "Ecuador", 
                         ridl = "data-should-be-on-ridl" ,
                                    thisyear = 2021 )
```

```{r tests-plot_reach_return}

```


## Chapter 2: Inclusion Capability

 1. How does the education enrollment of the refugee population compare with that of the local host population?
 
 2. How does the education attainment of the refugee population compare with that of the local host population?
 
 3. How does the professional profile composition of the refugee population compare with that of the local host population? 
 
 4. What are the main Professional Trajectory within the Refugee Population?
 

### 2.1 Education Enrollment


```{r function-plot_incl_educ_enroll}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#'   * "SE.PRE.ENRR", # School enrollment, preprimary -Age 3-5 (% gross) -
#'   * "SE.PRM.ENRR", # School enrollment, primary -Age 6 -11(% gross)  
#'   * "SE.SEC.ENRR", # School enrollment, secondary -Age 12-19 (% gross)
#'   * "SE.TER.ENRR" # School enrollment, tertiary -Age 20-24  (% gross) 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_incl_educ_enroll <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) {  
  
#levels(as.factor(Individual$EducationEnroll))
# "SE.PRE.ENRR", # School enrollment, preprimary -Age 3-5 (% gross) -
# "SE.PRM.ENRR", # School enrollment, primary -Age 6 -11(% gross)  
# "SE.SEC.ENRR", # School enrollment, secondary -Age 12-19 (% gross)
# "SE.TER.ENRR" # School enrollment, tertiary -Age 20-24  (% gross) 
  

Individual <- as.data.frame(progres[1] ) 
wb_data <- as.data.frame(progres[19] )

#wb_data$indicator_id

edEnroll <- Individual |> 
  dplyr::filter(!(is.na(Individual$EducationEnrollShould))) |> 
  dplyr::group_by(EducationEnroll  ) |> 
  dplyr::summarise(n = dplyr::n() ) |> 
  dplyr::filter(!(is.na( EducationEnroll)))  

#levels(as.factor(edEnroll$EducationEnroll))

ed <- Individual |> 
  dplyr::filter(!(is.na(Individual$EducationEnrollShould))) |> 
  
  dplyr::group_by(EducationEnrollShould ) |> 
  dplyr::summarise(n = dplyr::n(),
                   enrollatRightAge =  sum(EducationEnrollatRightAge == "yes"),
                   enrollNet = enrollatRightAge /n *100 ) |>
  
  dplyr::mutate( nEnrollCurrent = dplyr::case_when(
    EducationEnrollShould == "should.be.in.preprimary" ~ 
         as.integer(edEnroll[edEnroll$EducationEnroll=="is.in.preprimary", c("n")]),
    EducationEnrollShould == "should.be.in.primary" ~ 
      as.integer(edEnroll[edEnroll$EducationEnroll=="is.in.primary", c("n")]),       
    EducationEnrollShould == "should.be.in.secondary"  ~ 
      as.integer(edEnroll[edEnroll$EducationEnroll=="is.in.secondary", c("n")]),
    EducationEnrollShould == "should.be.in.tertiary"  ~ 
      as.integer(edEnroll[edEnroll$EducationEnroll=="is.in.tertiary", c("n")]) )) |> 
  dplyr::mutate(valueR = nEnrollCurrent /n *100 )  



dat <- ed |> 
  dplyr::mutate( #source = "UNHCR Primes",
    dateR =  2021 ) |>
  dplyr::mutate(indicator_id = dplyr::case_when(
    EducationEnrollShould == "should.be.in.preprimary" ~ "SE.PRE.ENRR",
    EducationEnrollShould == "should.be.in.primary" ~ "SE.PRM.ENRR",        
    EducationEnrollShould == "should.be.in.secondary" ~ "SE.SEC.ENRR",
    EducationEnrollShould == "should.be.in.tertiary" ~ "SE.TER.ENRR")) |> 
  dplyr::filter( indicator_id %in% wb_data$indicator_id) |>
  dplyr::select( indicator_id,dateR,  valueR ) |>
  #dplyr::arrange(desc(value)) |>
  dplyr::left_join(wb_data) |>
  dplyr::mutate(indicator  = dplyr::case_when(
    indicator_id == "SE.PRE.ENRR"  ~ "School enrollment, preprimary -Age 3-5", 
    indicator_id ==  "SE.PRM.ENRR"~ "School enrollment, primary -Age 6 -11",      
    indicator_id ==  "SE.SEC.ENRR"~ "School enrollment, secondary -Age 12-19", 
    indicator_id ==  "SE.TER.ENRR"~ "School enrollment, tertiary -Age 20-24")) |>  
  dplyr::mutate(indicator  = factor(indicator,
                                    levels = c("School enrollment, preprimary -Age 3-5",
                                               "School enrollment, primary -Age 6 -11",
                                               "School enrollment, secondary -Age 12-19",
                                               "School enrollment, tertiary -Age 20-24"))) |> 
  dplyr::filter( !(is.na(indicator)) )  

p <- dat |> 
  ggplot( ) + 
  geom_bar(aes(x = indicator, 
               y = value),
           fill = "gray80",
           stat = "identity") + 
  geom_bar(aes(x = indicator, 
               y = valueR),
           fill = "#0072bc", 
           width = .6,
           stat = "identity") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si(),
                      breaks= seq(0, 100, by = 20)) +
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = "How Education Enrollment of registered Population (blue) compare with Host?",
       subtitle = paste0("Percentage of kids enrolled at certain level vis a vis all kids that should in that level in ", ctr),   
       x = "",
       y = "As % (this can be more than 100%, as there might be more enrollment in a level than what the regular age group would imply)",
       caption = paste0( "Source: Data available in RIDL @ ",
                         ridl, 
                         " compared with baseline information for the country from UNESCO Institute for Statistics\n",
                        str_wrap( 
         "Note that UNHCR captures school attendance at time of registration, which is slightly different from the concept of Enrollment. Gross enrollment ratios indicate the capacity of each level of the education system, but a high ratio may reflect a substantial number of overage children enrolled in each grade because of repetition or late entry rather than a successful education system. The net enrollment rate excludes overage and underage students and more accurately captures the system's coverage and internal efficiency. Differences between the gross enrollment ratio and the net enrollment rate show the incidence of overage and underage enrollments  (see International Standard Classification of Education - ISCED). ", 
                         180)) ) 

return(p)
}

```


```{r examples-plot_incl_educ_enroll, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_incl_educ_enroll (progres = progres,
                                    ctr = "Ecuador" ,
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

```

```{r tests-plot_incl_educ_enroll}

```


### 2.2 Education Attainment

```{r function-plot_incl_educ_attain}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_incl_educ_attain <- function(progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) {   

Individual <- as.data.frame(progres[1] ) 
#levels(as.factor(Individual$EducationAttainment))
wb_data <- as.data.frame(progres[19] )

#table(Individual$EducationAttainment, useNA = "ifany")
Individual$EducationAttainment <- factor(Individual$EducationAttainment,
                                            levels = c("TER.DO","SEC.PO", 
                                                       "SEC.UP",
                                                       "SEC.LO", "PRM", "Not Measured"  ))


ed <- Individual |> 
  dplyr::filter( EducationAttainment != "Not Applicable") |> 
  dplyr::group_by(EducationAttainment ) |> 
  dplyr::summarise(n = dplyr::n()) #|>
  ## calculate cumulative 
  # dplyr::group_by(EducationAttainment ) |> 


p <- ed  |>
   dplyr::mutate(nCum =   
                dplyr::case_when(
                  EducationAttainment == "TER.DO" ~ n  ,
                  EducationAttainment == "SEC.PO" ~  
                          as.integer (ed  |> 
                                        dplyr::filter(EducationAttainment== "SEC.PO" ) |>
                                        dplyr::select(n) +
                                        ed  |> 
                                        dplyr::filter(EducationAttainment== "TER.DO" ) |>
                                        dplyr::select(n) ),  
                  EducationAttainment == "SEC.UP" ~  
                           as.integer (ed  |> 
                                       dplyr::filter(EducationAttainment== "SEC.LO" ) |>
                                       dplyr::select(n) +
                                         ed  |> 
                                         dplyr::filter(EducationAttainment== "TER.DO" ) |>
                                         dplyr::select(n) +
                                       ed  |> 
                                       dplyr::filter(EducationAttainment== "SEC.PO" ) |>
                                       dplyr::select(n) ),  
                  EducationAttainment == "SEC.LO" ~  
                          as.integer (ed  |> 
                                        dplyr::filter(EducationAttainment== "SEC.LO" ) |>
                                        dplyr::select(n) +
                                        ed  |> 
                                        dplyr::filter(EducationAttainment== "SEC.UP" ) |>
                                        dplyr::select(n) +
                                        ed  |> 
                                        dplyr::filter(EducationAttainment== "TER.DO" ) |>
                                        dplyr::select(n) +
                                        ed  |> 
                                        dplyr::filter(EducationAttainment== "SEC.PO" ) |>
                                        dplyr::select(n)  ),  
                  EducationAttainment == "PRM" ~  
                        as.integer (ed  |> 
                                      dplyr::filter(EducationAttainment== "SEC.LO" ) |>
                                      dplyr::select(n) +
                                      ed  |> 
                                      dplyr::filter(EducationAttainment== "PRM" ) |>
                                      dplyr::select(n) +
                                      ed  |> 
                                      dplyr::filter(EducationAttainment== "SEC.UP" ) |>
                                      dplyr::select(n) +
                                      ed  |> 
                                      dplyr::filter(EducationAttainment== "TER.DO" ) |>
                                      dplyr::select(n) +
                                      ed  |> 
                                      dplyr::filter(EducationAttainment== "SEC.PO" ) |>
                                      dplyr::select(n)   )
                  )) |>
  dplyr::mutate(valueR = round(nCum / sum(n) *100, 3)) |> 
    dplyr::mutate( #source = "UNHCR Primes",
                  dateR =  2021 ) |>
  dplyr::mutate(indicator_id = dplyr::case_when(
    EducationAttainment == "PRM" ~ "SE.PRM.CUAT.ZS",
    EducationAttainment == "SEC.LO" ~ "SE.SEC.CUAT.LO.ZS",        
    EducationAttainment == "SEC.UP" ~ "SE.SEC.CUAT.UP.ZS",
    EducationAttainment == "SEC.PO" ~ "SE.SEC.CUAT.PO.ZS",          
    EducationAttainment == "TER.DO" ~ "SE.TER.CUAT.DO.ZS")) |> 
  dplyr::filter( indicator_id %in% wb_data$indicator_id) |>
  dplyr::select( indicator_id,dateR,  valueR ) |>
  #dplyr::arrange(desc(value)) |>
  dplyr::left_join(wb_data) |>
  dplyr::mutate(indicator  = dplyr::case_when(
    indicator_id == "SE.PRM.CUAT.ZS"  ~ "At least completed primary", ## PRM + LO +UP + PO +DO
    indicator_id ==  "SE.SEC.CUAT.LO.ZS"~ "At least completed lower secondary (grade 6-9)", ## LO + UP + PO +DO      
    indicator_id ==  "SE.SEC.CUAT.UP.ZS"~ "At least completed upper secondary (grade 10-14)", ##  UP + PO +DO
    indicator_id ==  "SE.SEC.CUAT.PO.ZS"~ "At least completed post-secondary",  ## PO +DO         
    indicator_id ==  "SE.TER.CUAT.DO.ZS"~ "Doctoral or equivalent" )) |>  # DO
  dplyr::mutate(indicator  = factor(indicator,
                        levels = c("At least completed primary",
                                   "At least completed lower secondary (grade 6-9)",
                                   "At least completed upper secondary (grade 10-14)",
                                   "At least completed post-secondary",
                                   "Doctoral or equivalent"))) |> 
  dplyr::filter( !(is.na(indicator)) )  |> 
  ggplot( ) + 
  geom_bar(aes(x = indicator, 
               y = value),
           fill = "gray80",
           stat = "identity") + 
  geom_bar(aes(x = indicator, 
               y = valueR),
           fill = "#0072bc", 
           width = .6,
           stat = "identity") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = "How Education Attainment  of registered Population (blue) compare with Host?",
       subtitle = paste0("Attainement relates to the cumulative percentage of population ages 25 and over that attained certain levels in ",ctr),   
       x = "",
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl, " compared with baseline information for the country from UNESCO Institute for Statistics\n", str_wrap( 
         "A relative high concentration of the adult population in a given level of education reflects the capacity of the educational system in the corresponding level of education. Educational attainment is closely related to the skills and competencies of a country's population, and could be seen as a proxy of both the quantitative and qualitative aspects of the stock of human capital (see International Standard Classification of Education - ISCED).", 
         180)) ) 

return(p)
}

```


```{r examples-plot_incl_educ_attain, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_incl_educ_attain(progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) 

```

```{r tests-plot_incl_educ_attain}

```


### 2.3 Occupation Profile

```{r function-plot_incl_occup}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart . Build with isco http://www.harryganzeboom.nl/isco08/qa-isco-08.htm
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_incl_occup  <- function(progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
 Individual <- as.data.frame(progres[1] ) 

 p <- Individual |> 
  # dplyr::left_join(WorkExperience |>
  #                    dplyr::mutate(WorkExperience = WorkType) |>
  #                    dplyr::mutate(ModifiedOnWork = ModifiedOn) |>
  #                    dplyr::select(IndividualID, WorkExperience,ModifiedOnWork) ,
  #                  by = c("IndividualID")) |> 
  # dplyr::arrange(desc(ModifiedOnWork)) |> 
  # dplyr::filter(!duplicated(IndividualID, fromLast = FALSE)) |> 
  dplyr::group_by( WorkExperience  ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
  mutate(n = as.numeric(n), 
         nRound =  ifelse(n > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(n)),
                          as.character(n) ) ) |>
 dplyr::filter( ! (is.na(WorkExperience) )) |> 
  arrange(desc(n)) |>
  head(15) |> 
  ggplot( aes(x = reorder(WorkExperience, n),
              y = n )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
    ## Position label differently in the bar in white - outside bar in black
    geom_label( data =   function(x) subset(x, n < max(n) / 1.5),
                aes(x = reorder(WorkExperience, n),
                y = n,
                    label= nRound),
                hjust = -0.1 ,
                vjust = 0.5, 
                colour = "black", 
                fill = NA, 
                label.size = NA, 
                family = "Lato", 
                size = 4   ) +  
  
    geom_label( data =   function(x) subset(x, n >= max(n) / 1.5),
                aes(x = reorder(WorkExperience, n),
                y = n,
                    label= nRound),
                hjust = 1.1 ,
                vjust = 0.5, 
                colour = "white", 
                fill = NA, 
                label.size = NA, 
                family = "Lato", 
                size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = "What are the main type of work before asylum declared by registered individual?",
       subtitle = paste0("Among the ", scales::label_comma()(nrow(Individual)),
                         " records, ",
                         scales::label_comma()(nrow(Individual |>dplyr::filter( !(is.na(WorkExperience) )))),
                         " includes information on this topic in ", ctr),   
       x = "",
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl) ) 

return(p)

  }
```



```{r examples-plot_incl_occup, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_incl_occup(progres = progres ,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) 

```

```{r tests-plot_incl_occup}

```






###  2.4 Work Trajectory


```{r function-plot_incl_work}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_incl_work  <- function(progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
#
# names(WorkExperience)
# WorkExperience |> 
#   dplyr::group_by( WorkType, CountryOfWork   ) |> 
#   dplyr::summarise(n = dplyr::n()) |> 
#   mutate(n = as.numeric(n), 
#          nRound =  ifelse(n > 1000, 
#                            paste(scales::label_number_si(accuracy = 0.1)(n)),
#                            as.character(n) ) ) |>
#  dplyr::filter( ! (is.na(WorkType) )) |> 
#  dplyr::filter( CountryOfWork != ctr ) |> 
#   arrange(desc(n)) |>
#   head(10)  |> 
#   ggplot( aes(x = reorder(WorkType, n),
#               y = n )) + 
#   geom_bar(stat = "identity", 
#            fill = "#0072bc") + 
#   coord_flip() + 
#   scale_y_continuous( label = scales::label_number_si() ) + 
#     ## Position label differently in the bar in white - outside bar in black
#     geom_label( data =   function(x) subset(x, n < max(n) / 1.5),
#                 aes(x = reorder(WorkType, n),
#                 y = n,
#                     label= nRound),
#                 hjust = -0.1 ,
#                 vjust = 0.5, 
#                 colour = "black", 
#                 fill = NA, 
#                 label.size = NA, 
#                 family = "Lato", 
#                 size = 4   ) +  
#   
#     geom_label( data =   function(x) subset(x, n >= max(n) / 1.5),
#                 aes(x = reorder(WorkType, n),
#                 y = n,
#                     label= nRound),
#                 hjust = 1.1 ,
#                 vjust = 0.5, 
#                 colour = "white", 
#                 fill = NA, 
#                 label.size = NA, 
#                 family = "Lato", 
#                 size = 4   ) +    
#   scale_x_discrete(labels = function(x) {x |> str_wrap(40)}) +
#   geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
#   unhcrthemes::theme_unhcr( font_size= 18)  +  
#   theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
#         panel.grid.major.y  = element_blank(), 
#         panel.grid.minor = element_blank()) + 
#   labs(title = paste0("Top 10 Work Experience Type outside ", ctr),
#        subtitle = paste0("Among the ", scales::label_comma()(nrow(WorkExperience)),
#                          " records, ",
#                          scales::label_comma()(nrow(WorkExperience |>dplyr::filter( !(is.na(WorkType) )))),
#                          " includes information on this topic"),   
#        x = "",
#        y = "",
#        caption = paste0("Source: Data available in RIDL @ ", ridl) )
}

```


```{r examples-plot_incl_work, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_incl_work(progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

```

```{r tests-plot_incl_work}

```



## Chapter 3:  Main Protection Risk and Needs 

 1. __Gender__: Is there a higher-than-average percentage of women within registered case? 
 
 2. __Dependency__: Is there a higher-than-average percentage of Children and Older persons within registered case? 

 3. __Documentation__: What is the share of registered population with valid Document?

 4. __Specific Needs__: What the main Specific Needs 
 
 5. __Risk__: How combination of needs are combined?
  

### 3.1 How well documented is the population?

```{r function-plot_prot_doc}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_prot_doc  <- function(progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
#names(Document)
#levels(as.factor(Document$DocumentType))


Individual <- as.data.frame(progres[1] ) 
Document <-  as.data.frame(progres[4] )

p <- Individual |> 
  dplyr::filter( LegalStatus != "Not of concern" ) |> 
  #names(Individual)
  dplyr::select(IndividualID, Age, AgeCohort, Sex, LegalStatus ) |> 
  dplyr::left_join(Document) |> 
  
  ## Add something for individuals that have no linked doc
  dplyr::mutate( DocumentType = dplyr::if_else(is.na(DocumentType), "No records of Document", DocumentType)) |> 
  ## Clean record with "-"
  dplyr::mutate( DocumentType = dplyr::if_else(DocumentType== "-", "Unknown (no event)" , DocumentType)) |> 
  ## Clean Document type
  dplyr::mutate(DocumentType = str_replace(DocumentType, " \\(no event\\)", ""))  |> 
  ## Concat document type and status
  dplyr::mutate( doctypestatus = paste0( DocumentType,
                                         dplyr::if_else(is.na(DocumentStatus), " ", 
                                                        paste0(" / ",  DocumentStatus) ))) |> 
  ## clean potential duplicate
  dplyr::distinct(IndividualID, doctypestatus, .keep_all = TRUE)  |>   
  
  dplyr::group_by( doctypestatus  ) |> 
  dplyr::summarise(cnt = dplyr::n())    |> 
  dplyr::mutate( totalind = nrow(Individual |> 
                                   dplyr::filter( LegalStatus != "Not of concern" )),
                 n = cnt/totalind  )    |>  # 
  dplyr::mutate(n = as.numeric(n), 
         nRound =  paste0( scales::label_number_si(accuracy = 0.1)(n*100),  "%"))    |>
  dplyr::mutate(flag = dplyr::if_else(doctypestatus == "No records of Document ", "yes",   "no" ))    |>
  #dplyr::filter( ! (is.na(doctypestatus) )) |> 
  arrange(desc(n)) |>
  head(15)    |> 
  ggplot( aes(x = reorder(doctypestatus,n), 
              y = n,
              fill = flag)) + 
  guides(fill= "none") +
  scale_colour_manual(values = c("#0072bc", "#CCCCCC"),
                      aesthetics = c("colour", "fill")) +
  geom_bar(stat = "identity" ) + 
          # fill = "#0072bc") + 
  coord_flip() + 
  scale_y_continuous(labels=scales::percent, breaks= seq(0, 1, by = 0.2)) +
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, n < max(n) / 1.5),
              aes(x = reorder(doctypestatus, n),
                  y = n,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, n >= max(n) / 1.5),
              aes(x = reorder(doctypestatus, n),
                  y = n,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = "What type of documentation registered individuals have? ",
       subtitle = paste0("Top 15 Documentation type & status in ",ctr),   
       x = "",
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl, "\n One individual can actually have more than one type of document, except when there is No records of Document") )

 return(p)
  
  ## Add annotation -- use ggannotate to get the right  coordinate within chart
  #remotes::install_github("mattcowgill/ggannotate")
  #ggannotate::ggannotate()
  
  # geom_curve(aes(xend = 10.9476141263782, yend = 2959.93589579213, 
  #                x = 6.91965137456717, y = 28668.752697603),
  #            size = 2, color = "tan",
  #            arrow = arrow(length = unit(0.07, "npc"))) +
  # ggtext::geom_textbox(data = data.frame(x = 6.91965137456717, y = 28668.752697603, 
  #                                        label = "Why so many people are using **other** category? \n Is there an important missing category within Primes?"),
  #                     mapping = aes(x = x, y = y, label = label),
  #                     width = unit(0.6, "npc"),
  #                     family = "Lato", size = 7, fill = "cornsilk",
  #                     inherit.aes = FALSE)
}

```


```{r examples-plot_prot_doc, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_prot_doc (progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )
```

```{r tests-plot_prot_doc}

```


### 3.2 Women & Dependency  Ratio 


```{r function-plot_prot_ratio}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_prot_ratio  <- function(progres,
                                    ctr ,
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
  
  RegistrationGroupall <-  as.data.frame(progres[17]) 
  
pfemaleRat <- RegistrationGroupall |> 
  dplyr::group_by( ratio_female_cat  ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
  mutate(n = as.numeric(n), 
         nRound =  ifelse(n > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(n)),
                          as.character(n) ) ) |>
 dplyr::filter( ! (is.na(ratio_female_cat) )) |> 
  arrange(desc(n)) |>
  head(15)  |> 
 ggplot( aes(x = ratio_female_cat, 
            y = n )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, n < max(n) / 1.5),
              aes(x = ratio_female_cat,
                  y = n,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, n >= max(n) / 1.5),
              aes(x = ratio_female_cat,
                  y = n,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = " ",
       subtitle = paste0("Proportion of Female "),   
       x = "",
       y = "" ) 

pyouthRat <- RegistrationGroupall |> 
  dplyr::group_by( ratio_youth_cat  ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
  mutate(n = as.numeric(n), 
         nRound =  ifelse(n > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(n)),
                          as.character(n) ) ) |>
 dplyr::filter( ! (is.na(ratio_youth_cat) )) |> 
  arrange(desc(n)) |>
  head(15)  |> 
  ggplot( aes(x = ratio_youth_cat, 
              y = n )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, n < max(n) / 1.5),
              aes(x = ratio_youth_cat,
                  y = n,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, n >= max(n) / 1.5),
              aes(x = ratio_youth_cat,
                  y = n,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = " ",
       subtitle = paste0("Youth Dependency"),   
       x = "",
       y = "" ) 


peldernRat <- RegistrationGroupall |> 
  dplyr::group_by( ratio_eldern_cat  ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
  mutate(n = as.numeric(n), 
         nRound =  ifelse(n > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(n)),
                          as.character(n) ) ) |>
 dplyr::filter( ! (is.na(ratio_eldern_cat) )) |> 
  arrange(desc(n)) |>
  head(15)  |> 
  ggplot( aes(x = ratio_eldern_cat, 
              y = n )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, n < max(n) / 1.5),
              aes(x = ratio_eldern_cat,
                  y = n,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, n >= max(n) / 1.5),
              aes(x = ratio_eldern_cat,
                  y = n,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = " ",
       subtitle = paste0("Eldern Dependency"),   
       x = "",
       y = "" ) 


require(patchwork)
p <- pfemaleRat  + 
        pyouthRat +  
        peldernRat  + 
        plot_annotation(
              title = paste0("What are the Case composition Ratio within each Registered Group in ", ctr, "?"),
              caption = paste0("Source: Data available in RIDL @ ", ridl, "\n. This information can provide an initial overview of potential vulnerabilities within the case load.") )
              
return(p)

}
```


```{r examples-plot_prot_ratio, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")

plot_prot_ratio (progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

```

```{r tests-plot_prot_ratio}

```


### 3.3 Specific Need  Sub Category by case

```{r function-plot_prot_spneedcat}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'

plot_prot_spneedcat  <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
  
  

 Individual <- as.data.frame(progres[1] ) 
 SpecificNeed <-  as.data.frame(progres[14] )
 RegistrationGroup <- as.data.frame(progres[2] )
  RegistrationGroupall <-  as.data.frame(progres[17])

p <- SpecificNeed |> 
  dplyr::left_join( y = Individual,
                    by = c("IndividualID")) |> 
  dplyr::group_by( RegistrationGroupID, SpecificNeedSub   ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
 dplyr::filter( ! (is.na(SpecificNeedSub) ))  |> 
 dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
  dplyr::group_by( SpecificNeedSub  ) |> 
  dplyr::summarise(uniquecase = dplyr::n())  |>    
  dplyr::arrange(desc(uniquecase)) |>
  head(15)  |> 

  dplyr::left_join(SpecificNeed |> 
                     dplyr::left_join( y = Individual,
                                       by = c("IndividualID")) |> 
                     dplyr::group_by( RegistrationGroupID, SpecificNeedSub   ) |> 
                     dplyr::summarise(n = dplyr::n()) |> 
                    dplyr::filter( ! (is.na(SpecificNeedSub) ))  |> 
                    dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
                     dplyr::group_by( SpecificNeedSub  ) |> 
                     dplyr::summarise(totalind = sum(n))
  ) |> 
  dplyr::mutate(avgindpercase = totalind/uniquecase)   |>
  mutate(uniquecase = as.numeric(uniquecase), 
       nRound =  ifelse(uniquecase > 1000, 
                        paste(scales::label_number_si(accuracy = 0.1)(uniquecase)),
                        as.character(uniquecase) ) ) |>  
  ggplot( aes(x = reorder(SpecificNeedSub,uniquecase), 
              y = uniquecase )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, uniquecase < max(uniquecase) / 1.5),
              aes(x = reorder(SpecificNeedSub, uniquecase),
                  y = uniquecase,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, uniquecase >= max(uniquecase) / 1.5),
              aes(x = reorder(SpecificNeedSub, uniquecase),
                  y = uniquecase,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = paste0("What are the main occurence of Specific Needs at case level in ", ctr, "?"),
       subtitle = paste0("Among the ", scales::label_comma()(nrow(RegistrationGroup)),
                         " case records, ",
                         scales::label_comma(accuracy = .1)(nrow(RegistrationGroupall |>dplyr::filter(countneed =="FALSE")) / nrow(RegistrationGroupall ) *100) ,
                         " % of cases have no single associated records of specific needs"),   
       x = "",
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl ,  "\n",
         str_wrap( 
         "This chart presents only the top 15 most frequent specific needs - type and subtype - measured in terms of occurence at case level (i.e. at least one record). One Individual can have more than one specific needs.",
           180) )) 

 return(p)

}

```


```{r examples-plot_prot_spneedcat, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_prot_spneedcat  (progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

```

```{r tests-plot_prot_spneedcat}

```


### 3.4 Association of specific needs

```{r function-plot_prot_spneedass}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_prot_spneedass  <- function(progres,
                                    ctr  ,
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
Individual <- as.data.frame(progres[1] ) 
SpecificNeed <-  as.data.frame(progres[14] )
  
topneeds <- as.vector(as.data.frame(SpecificNeed |> 
  dplyr::left_join( y = Individual,
                    by = c("IndividualID")) |> 
  dplyr::group_by( RegistrationGroupID, SpecificNeedSub   ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
 dplyr::filter( ! (is.na(SpecificNeedSub) ))  |> 
 dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
  dplyr::group_by( SpecificNeedSub  ) |> 
  dplyr::summarise(uniquecase = dplyr::n())  |>    
  dplyr::arrange(desc(uniquecase)) |>
  head(15) |>
  dplyr::select(SpecificNeedSub)   ))  |>
  as.data.frame() |>
  dplyr::pull()

 
d1 <- SpecificNeed |> 
  dplyr::filter(SpecificNeedSub  %in%  topneeds ) |>
  dplyr::left_join( y = Individual,
                    by = c("IndividualID")) |> 
  dplyr::group_by( RegistrationGroupID, SpecificNeedSub   ) |> 
  dplyr::summarise(n = dplyr::n())  |> 
 dplyr::filter( ! (is.na(RegistrationGroupID) ))  |>
  tidyr::pivot_wider(names_from  = SpecificNeedSub,
                     values_from = n) #|> 
d <- d1  |> 
  dplyr::mutate( dplyr::across(where(is.integer), ~ tidyr::replace_na(.x, 0)) )# |>
 #replace(is.na(.), 0)
 # mutate(  across(everything(), ~replace_na(.x, 0))  )

# d  |>
#   dplyr::ungroup() |>
#   dplyr::select( - 1 ) |> 
#   corrr::correlate() |> 
#   corrr::network_plot(min_cor = 0.3)

d2 <- d  |>
  dplyr::ungroup() |>
  dplyr::select( - 1 )  

# Create a tidy data frame of correlations
corr <- d2 |> 
  corrr::correlate() 

corrMat <- round(cor(d2), 1)
p.mat <- ggcorrplot::cor_pmat(d2)
#corrr::correlate(d2) 

p <- ggcorrplot::ggcorrplot(  corrMat  ,
           hc.order = TRUE,
           type = "lower",
            method = "circle",
           outline.col = "white",
           ggtheme = ggplot2::theme_gray,
           colors = c("#6D9EC1", "white", "#E46726") ,
           ## cross if not significant
            p.mat = p.mat) + 
   guides(fill= "none") +
  unhcrthemes::theme_unhcr( font_size= 12)  +  
   theme(axis.text.x = element_text(size = 8, angle = 40,  hjust=1),
        axis.text.y = element_text(size = 8) ) +
  labs(
    y = "",
    x = " ",
    title = paste0("What are the main Associations between different types of Specific needs in ", ctr, "?"),
    subtitle = str_wrap( 
      "Correlation analysis: Red color indicate a positive association, while blue a negative one. The bigger the dot, the stronger the association, cross indicates the absence of significative association",
      180) ,
    caption = paste0("Source: Data available in RIDL @ ", ridl, "")
  )
return(p)

# tidy_cors <-corr |> 
#   corrr::stretch()
# 
# 
# # Convert correlations stronger than some value
# # to an undirected graph object
# graph_cors <- tidy_cors |>
#  dplyr::filter(abs(r) > .1) |>
#   igraph::graph_from_data_frame(directed = FALSE)
# 
# # Plot
# ggraph(graph_cors) +
#   geom_edge_link(aes(edge_alpha = abs(r),
#                      edge_width = abs(r), 
#                      color = r)) +
#   guides(edge_alpha = "none", 
#          edge_width = "none") +
#   scale_edge_colour_gradientn(limits = c(-1, 1), 
#                               # colors = c("firebrick2",
#                               #            "dodgerblue2")
#                               colors = c("blue", "gray90",  "red")
#                               ) +
#   geom_node_point(color = "gray90", 
#                   size = 7) +
#   geom_node_text(aes(label = name), 
#                  repel = TRUE) + 
#   unhcrthemes::theme_unhcr( font_size= 18)  +  
#   theme(panel.grid.major.x  = element_blank(), 
#         panel.grid.major.y  = element_blank(), 
#         panel.grid.minor = element_blank(), 
#         axis.text.x =  element_blank(), 
#         axis.text.y = element_blank(), 
#         legend.key.height= unit(0.5, 'cm'),
#         legend.key.width= unit(3, 'cm') ) +
#   labs(
#     y = "",
#     x = " ",
#     title = paste0("What are the main Association between different types of Specific needs in ", ctr, "?"),
#     subtitle = paste0("Correlation analysis: Red color indicate a positive association, while blue a negative one. "),
#     caption = paste0("Source: Data available in RIDL @ ", ridl, "")
#   )
}
```


```{r examples-plot_prot_spneedass, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")

plot_prot_spneedass (progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

```

```{r tests-plot_prot_spneedass}

```


## Chapter 4: Population Segmentation


 * Since the 70's, Social scientist have developed __data exploratory__ techniques that allow to discover statistical segments among a specific population. Those techniques are commonly used in __marketing studies__.

 * To do that, Clustering analysis aims to group a set of records in such a way that records in the same group are more similar to each other than to those in other groups. [Multiple Correspondence Analysis (MCA)](https://en.wikipedia.org/wiki/Multiple_correspondence_analysis) together with [Hierarchical Classification on Principle Components](http://factominer.free.fr/classical-methods/hierarchical-clustering-on-principal-components.html) can be used to process together multiple categorical data  in order to detect and represent the __underlying structures__ in a data set. 

 * This aims at generating induction rather than testing an hypothesis according to model. The resulting segments should be interpreted as broad categories (rather than a criteria-based classification) that can then help informing programme design and subsequent __theories of change__ for each segments.
 


### 4.1 Variables to segment the population

```{r function-plot_segment_var}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart performing unsupervised classification on a series of key variables 
#'  https://www.datanovia.com/en/blog/cluster-analysis-in-r-simplified-and-enhanced/  
#'  https://www.datanovia.com/en/lessons/cluster-validation-statistics-must-know-methods/
#'  See video https://www.youtube.com/watch?v=0z30RDikYaw
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_segment_var  <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
  
  
     RegistrationGroupall <-  as.data.frame(progres[17]) 
     ## Step 1: Select variables used for clustering
     data2cluster <- RegistrationGroupall[,  c("group_size1", 
                  "ratio_female_cat",
                  "sex_fp",
                  "ratio_dependant_cat",
                  "age_sd_cat",  
                    "divorced_separated_widow",                         
                     "single_adult" , "single_minor" , "child_at_risk" ,
                    "married_engaged", "disability" ,
                    "specific_legal_and_physical_protection_needs",  
                    "serious_medical_condition", "sgbv" )] |>
  dplyr::mutate_if(is.integer,as.factor) |>
  dplyr::mutate_if(is.numeric,as.factor)|>
  dplyr::mutate_if(is.logical,as.factor)

samplesize <- 10000
data.sample <- data2cluster[sample(1:nrow(data2cluster), 
                            samplesize,
                            replace=FALSE), ]

## Step 2: perform Multiple correspondance analysis
data.mca <- FactoMineR::MCA(data.sample, graph= FALSE)

## Step 3: Hierarchical Classification
data.mca.hcpc <- FactoMineR::HCPC(data.mca, 
                                  nb.clust=-1, 
                                  min=3, 
                                  max=4, 
                                  graph=FALSE, 
                                  order=FALSE, 
                                  consol=TRUE, 
                                  kk=1000)

## Predict projection for new rows with Multiple Correspondence Analysis
#data.predict <- predict(data.mca, data2cluster)

## Step 4:  Associate group with clusters
cluster <- data.mca.hcpc$data.clust
cluster$clust <- as.character(cluster$clust)
cluster$clust[cluster$clust==1] <- "Segment 1"
cluster$clust[cluster$clust==2] <- "Segment 2"
cluster$clust[cluster$clust==3] <- "Segment 3"
cluster$clust[cluster$clust==4] <- "Segment 4"
cluster$clust <- as.factor(cluster$clust)

### Now create a patchwork with key plots from this 
## plot 1 with variable
pvar <- factoextra::fviz_mca_var(data.mca, 
                                 labelsize = 3, 
                                 repel = TRUE,
                                 pointsize = 0, 
                                 select.var = list(contrib = 15)) +
  labs(title = "Representation of variables proximity" )  +   
  labs(caption = "This charts display the results of Multiple Correspondance Analysis (MCA)") +
  unhcrthemes::theme_unhcr( font_size= 12)

## plot2 with cluster 
pclust <- factoextra::fviz_cluster(data.mca.hcpc,
                                   # repel = TRUE,  # Avoid label overlapping
                                   geom = "point",
                                   show.clust.cent = TRUE, # Show cluster centers
                                   palette = "jco", # Color palette see ?ggpubr::ggpar
                                   ggtheme = theme_minimal(),
                                   main = "Representation of population segment")+ 
  unhcrthemes::theme_unhcr( font_size= 12) +
  labs(caption = "This charts display the results of Hierarchical Clustering on Principal Components (HCPC)") 

## plot3 with cluster proportion
pclustprop <- ggplot(cluster, aes(x=clust)) +
  geom_bar(aes(y = ..count.. / sapply(PANEL, FUN=function(x) sum(count[PANEL == x]))),
           fill="#2a87c8",colour="#2a87c8") +
  #facet_wrap(~subgov, ncol=4) +
  guides(fill= "none") +
  ylab("Frequency") +
  scale_y_continuous(labels=scales::percent, breaks= seq(0, 1, by = 0.1)) +
  coord_flip() +
  labs( title = paste0("Share of each Population Segment in ", ctr),
       x = "", 
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl, "") ) + 
  unhcrthemes::theme_unhcr( font_size= 12)  +    
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank())

## Now display the 3 charts within one single ggplot2 object with patchwork
 require(patchwork)
 p <- pvar | (pclust / pclustprop)
 
 cluster <- list( p, data.mca.hcpc)
 
 return(cluster)

}

```


```{r examples-plot_segment_var, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
cluster <- plot_segment_var(progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

cluster[[1]]

```

```{r tests-plot_segment_var}

```


### 4.2 Description of each population segment

```{r function-plot_segment_group}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart with clusters relative description:
#' The variable modalities in each of the profiles can be __interpreted__ using the following information:  
#'   * _Cla/Mod_ is the pourcentage of records who have that modality and who are in that the profile (for instance: 50.3% of the cases who have a head of family who marrital status is single also belongs to profile 1) 
#'   * _Mod/Cla_ is the pourcentage of records in that profile who have that modality (for instance: 81.5% of the cases of profile  1 have a head of family who marrital status is single ) 
#'   * _Global_ is the global pourcentage of all records who have that modality (for instance: in all population, 51.67% of of the cases who have a head of family who marrital status is single.) 
#'   * _p-value_ provides an idea of the significant of the difference between Mod/Cla proportation & Global. If p-value is less than 0.05, then one category is significantly linked to another categories  
#'   * _v-test_ If the v-test is positive, it means that the category is over-expressed for the category and if the v-test is negative it means that the category is under-expressed for the category.What is interesting in the v-test is only the sign of the v-test. 
#'   
#'   Only variable modalities for which critical probability is below 0.02 are used."  
#'   
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_segment_group  <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
  
  cluster <- plot_segment_var(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

   data.mca.hcpc <- cluster[2]
# aggregate modalitied description of each segment
segments <- as.data.frame(data.mca.hcpc$desc.var$category$`1`) |>
  janitor::clean_names()  |>
  dplyr::mutate(mod = row.names(.))  |>
  dplyr::mutate(mod2 = gsub(".*=", "", mod)) |>
  dplyr::mutate(varcat = gsub("=.*", "", mod)) |>
  dplyr::mutate(segment = "Segment 1") |>
  rbind( as.data.frame(data.mca.hcpc$desc.var$category$`2`) |>
           janitor::clean_names()  |>
           dplyr::mutate(mod = row.names(.))  |>
           dplyr::mutate(mod2 = gsub(".*=", "", mod)) |>
           dplyr::mutate(varcat = gsub("=.*", "", mod)) |>
           dplyr::mutate(segment = "Segment 2") ) |>
  rbind( as.data.frame(data.mca.hcpc$desc.var$category$`3`) |>
           janitor::clean_names()  |>
           dplyr::mutate(mod = row.names(.))  |>
           dplyr::mutate(mod2 = gsub(".*=", "", mod)) |>
           dplyr::mutate(varcat = gsub("=.*", "", mod)) |>
           dplyr::mutate(segment = "Segment 3") ) |>
  rbind( as.data.frame(data.mca.hcpc$desc.var$category$`4`) |>
           janitor::clean_names()  |>
           dplyr::mutate(mod = row.names(.))  |>
           dplyr::mutate(mod2 = gsub(".*=", "", mod)) |>
           dplyr::mutate(varcat = gsub("=.*", "", mod)) |>
           dplyr::mutate(segment = "Segment 4") ) |>
  dplyr::mutate(mod_cla = mod_cla / 100)|>
  dplyr::mutate(cla_mod = cla_mod / 100)|>
  dplyr::mutate(global = global / 100) 

# now plotting this 
p <- ggplot(segments ) + 
  geom_col(aes(x = reorder(mod2,mod_cla), 
               y = cla_mod), fill="grey", width=0.5) + 
  geom_col(aes(x = reorder(mod2,mod_cla), 
               y = mod_cla), width=0.2) + 
  geom_errorbar(aes(x = reorder(mod2,mod_cla), 
                    y = global,
                    ymin = global,
                    ymax= global), 
                width = .45) + 
    scale_y_continuous(labels=scales::percent, breaks= seq(0, 1, by = 0.5)) +
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  coord_flip() +  
  #facet_grid(varcat ~ ., scales = "free", space = "free") +
   facet_grid(. ~ segment ) +
  #facet_grid(vars(varcat), vars(segment)) +
 # facet_grid(vars(varcat) ) +
  unhcrthemes::theme_unhcr( font_size= 16)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank(),
        strip.text.y = element_text(angle = 0),
        axis.text.x = element_text(size = 10)) + 
  labs(title = "Comparing the Characteristics of each Segments",
       subtitle =  "Modalities Distribution per Segment" ,   
       x = "",
       y = "",
       caption = paste0(str_wrap( 
         "In Black: Modality in Class  is the percentage of records in that profile who have that modality", 
         160), "\n",
         str_wrap( 
         "In Grey: Class in Modality is the percentage among all records who have that modality and who are in that the profile", 
           160), "\n",
         str_wrap( 
         "As line: Global is the global percentage of all records who have that modality ",
           160) ) ) 

return(p)


}
```


```{r examples-plot_segment_group, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

#progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
# progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
# plot_segment_group(progres = progres,
#                                     ctr = "Ecuador",
#                                     ridl = "data-should-be-on-ridl",
#                                     thisyear = 2021 ) 
```

```{r tests-plot_segment_group}

```


## Chapter 5: Assistance & Targeting

 1. What main types of Assistance are being recorded?  
 
 2. How much Assistance Interventions have evolved over time?

 3. What is the specific profile of assisted by type of assistance?
 
 4. How much different assistance types are being Combined? 
 
 5. What the main characteristics of those who a registered but not assisted?



### 5.1 What are the main types of Assistance provided by Case?

```{r function-plot_assist_type}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_assist_type <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
  
  

Individual <- as.data.frame(progres[1] ) 
Assistance <-  as.data.frame(progres[3] )
     RegistrationGroupall <-  as.data.frame(progres[17]) 
  
p <- Assistance |> 
  #filter( AssistanceYear == 2020) |> 
  dplyr::left_join( y = Individual,
                    by = c("IndividualID", "RegistrationGroupID")) |> 
  dplyr::group_by( RegistrationGroupID, AssistanceSub   ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
 dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
 dplyr::filter( ! (is.na(AssistanceSub) ))  |> 
  dplyr::group_by( AssistanceSub  ) |> 
  dplyr::summarise(uniquecase = n())   |> 
  
  dplyr::left_join(Assistance |> 
                     #dplyr::filter( AssistanceYear == 2020) |> 
                     dplyr::left_join( y = Individual,
                                       by = c("IndividualID", "RegistrationGroupID")) |> 
                     dplyr::group_by( RegistrationGroupID, AssistanceSub   ) |> 
                     dplyr::summarise(n = dplyr::n()) |> 
                    dplyr::filter( ! (is.na(AssistanceSub) ))  |> 
                    dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
                     dplyr::group_by( AssistanceSub  ) |> 
                     dplyr::summarise(totalind = sum(n)) )  |> 
  dplyr::mutate(avgindpercase = totalind/uniquecase)     |>
  dplyr::mutate(totalcase = nlevels(as.factor(Individual$RegistrationGroupID)))  |>
  dplyr::mutate(assistcover = uniquecase/totalcase)     |>
  dplyr::filter(assistcover >= 0.01 )     |>
  mutate(uniquecase = as.numeric(uniquecase), 
         nRound =  ifelse(uniquecase > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(uniquecase)),
                          as.character(uniquecase) ) ) |>  
  ggplot( aes(x = reorder(AssistanceSub,uniquecase), 
              y = uniquecase )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  coord_flip() + 
  scale_y_continuous( label = scales::label_number_si() ) + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, uniquecase < max(uniquecase) / 1.5),
              aes(x = reorder(AssistanceSub, uniquecase),
                  y = uniquecase,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, uniquecase >= max(uniquecase) / 1.5),
              aes(x = reorder(AssistanceSub, uniquecase),
                  y = uniquecase,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = paste0("What are the main type of recorded Assistance in ", ctr, "?"),
       subtitle = paste0("There's a total of  ", scales::label_comma()(nrow(Assistance)),
                         " assistance records, ",
                         scales::label_comma(accuracy = .1)(nrow(RegistrationGroupall |>
                                                                   dplyr::filter(got_assistance== "FALSE")) / nrow(RegistrationGroupall ) *100) ,
                         " % of cases have no single associated records of assistance"),   
       x = "",
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl, "\n Record are counted as single occurence per type at case level.") ) 

return(p)
}

```


```{r examples-plot_assist_type, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
# progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_assist_type (progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) 
```

```{r tests-plot_assist_type}

```


### 5.2  How much Assistance Interventions have evolved over time?

```{r function-plot_assist_evol}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
plot_assist_evol  <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 

Individual <- as.data.frame(progres[1] ) 
Assistance <-  as.data.frame(progres[3] )
     RegistrationGroupall <-  as.data.frame(progres[17]) 

topAssistanceSub <- as.vector(as.data.frame(Assistance |> 
                                              dplyr::left_join( y = Individual,
                                                                by = c("IndividualID", "RegistrationGroupID")) |> 
                                              dplyr::group_by( RegistrationGroupID, AssistanceSub   ) |> 
                                              dplyr::summarise(n = dplyr::n()) |> 
                                             dplyr::filter( ! (is.na(AssistanceSub) ))  |> 
                                             dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
                                              dplyr::group_by( AssistanceSub  ) |> 
                                              dplyr::summarise(uniquecase = dplyr::n())  |>    
                                              dplyr::arrange(desc(uniquecase)) |>
                                              head(15) |>
                                              dplyr::select(AssistanceSub)   )) |>
                                              as.data.frame() |>
                                               dplyr::pull()



p <- Assistance |>   
  dplyr::filter(AssistanceSub  %in%  topAssistanceSub ) |>
  dplyr::left_join( y = Individual,
                    by = c("IndividualID", "RegistrationGroupID")) |> 
  dplyr::group_by( RegistrationGroupID, AssistanceSub, AssistanceYear   ) |> 
  dplyr::summarise(n = dplyr::n())  |> 
 dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
 dplyr::filter( ! (is.na(AssistanceSub) ))  |> 
  dplyr::group_by( AssistanceSub, AssistanceYear  ) |> 
  dplyr::summarise(uniquecase = n())  |> 
  
  dplyr::left_join(
    Assistance |> 
      dplyr::filter(AssistanceSub  %in%  topAssistanceSub ) |>
      dplyr::left_join( y = Individual,
                        by = c("IndividualID", "RegistrationGroupID")) |> 
      dplyr::group_by( RegistrationGroupID, AssistanceSub, AssistanceYear    ) |> 
      dplyr::summarise(n = dplyr::n()) |> 
     dplyr::filter( ! (is.na(AssistanceSub) ))  |> 
     dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
      dplyr::group_by( AssistanceSub, AssistanceYear   ) |> 
      dplyr::summarise(totalind = sum(n))
  ) |> 
  dplyr::mutate(avgindpercase = totalind/uniquecase)     |>
  dplyr::mutate(totalcase = nlevels(as.factor(Individual$RegistrationGroupID)))  |>
  dplyr::mutate(assistcover = uniquecase/totalcase)    |>
  dplyr::filter(AssistanceYear >= 2019 )     |>
  dplyr::filter( !(is.na(AssistanceYear)) )     |>
  mutate(uniquecase = as.numeric(uniquecase), 
         nRound =  ifelse(uniquecase > 1000, 
                          paste(scales::label_number_si(accuracy = 0.1)(uniquecase)),
                          as.character(uniquecase) ) ) |>  
  ggplot( aes(x = reorder(AssistanceSub,uniquecase), 
              y = uniquecase )) + 
  geom_bar(stat = "identity", 
           fill = "#0072bc") + 
  coord_flip() + 
  facet_grid(. ~ AssistanceYear  ) +
  scale_y_continuous( label = scales::label_number_si() ) + 
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data =   function(x) subset(x, uniquecase < max(uniquecase) / 1.5),
              aes(x = reorder(AssistanceSub, uniquecase),
                  y = uniquecase,
                  label= nRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +  
  
  geom_label( data =   function(x) subset(x, uniquecase >= max(uniquecase) / 1.5),
              aes(x = reorder(AssistanceSub, uniquecase),
                  y = uniquecase,
                  label= nRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              family = "Lato", 
              size = 4   ) +   
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank()) + 
  labs(title = paste0("How Assistance assistance intervention changed in ", ctr, "?"),
       subtitle = paste0("Evolution since 2019 for top 15 most frequent types of intervention"),   
       x = "",
       y = "",
       caption = paste0("Source: Data available in RIDL @ ", ridl, "\n Record are counted as single occurence per type at case level.") )
return(p)

}

```


```{r examples-plot_assist_evol, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
# progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
plot_assist_evol(progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

```

```{r tests-plot_assist_evol}

```


### 5.3 How different type of Assistance are combined?

```{r function-plot_assist_combin}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
plot_assist_combin  <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
  
  

Individual <- as.data.frame(progres[1] ) 
Assistance <-  as.data.frame(progres[3] )
 RegistrationGroupall <-  as.data.frame(progres[17]) 

topAssistanceSub <- as.vector(as.data.frame(Assistance |> 
  dplyr::left_join( y = Individual,
                     by = c("IndividualID", "RegistrationGroupID")) |> 
  dplyr::group_by( RegistrationGroupID, AssistanceSub   ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
  dplyr::filter( ! (is.na(AssistanceSub) ))  |> 
  dplyr::filter( ! (is.na(RegistrationGroupID) ))   |> 
  dplyr::group_by( AssistanceSub  ) |> 
  dplyr::summarise(uniquecase = dplyr::n())  |>    
  dplyr::arrange(desc(uniquecase)) |>
  head(15) |>
  dplyr::select(AssistanceSub)   )) |>
  as.data.frame() |>
  dplyr::pull()

d1 <- Assistance |> 
  dplyr::filter(AssistanceSub  %in%  topAssistanceSub ) |>
  #filter( AssistanceYear == 2020) |> 
  dplyr::left_join( y = Individual,
                    by = c("IndividualID", "RegistrationGroupID")) |> 
  dplyr::group_by( RegistrationGroupID, AssistanceSub   ) |> 
  dplyr::summarise(n = dplyr::n()) |> 
 dplyr::filter( ! (is.na(RegistrationGroupID) ))  |>
  tidyr::pivot_wider(names_from  = AssistanceSub,
                     values_from = n)
d <- d1  |> 
  dplyr::mutate( dplyr::across(where(is.integer), ~ tidyr::replace_na(.x, 0)) )
  #replace(is.na(.), 0)
  ## Remove identifiers
d2 <- d  |>
  dplyr::ungroup() |>
  dplyr::select( - 1 )  

corrMat <- round(cor(d2), 1)
p.mat <- ggcorrplot::cor_pmat(d2)
#corrr::correlate(d2) 

p <- ggcorrplot::ggcorrplot(  corrMat  ,
           hc.order = TRUE,
           type = "lower",
            method = "circle",
           outline.col = "white",
           ggtheme = ggplot2::theme_gray,
           colors = c("#6D9EC1", "white", "#E46726") ,
           ## cross if not significant
            p.mat = p.mat) + 
   guides(fill= "none") +
  unhcrthemes::theme_unhcr( font_size= 12)  +  
   theme(axis.text.x = element_text(size = 8, angle = 40,  hjust=1),
        axis.text.y = element_text(size = 8) ) +
  labs(
    y = "",
    x = " ",
    title = paste0("How much different types of Assistance aggregated at Case level are associated in ", ctr, "?"),
    subtitle = str_wrap( 
      "Correlation analysis: Red color indicate a positive association, while blue a negative one. The bigger the dot, the stronger the association, cross indicates the absence of significative association",
      180) ,
    caption = paste0("Source: Data available in RIDL @ ", ridl, "")
  )
return(p)


# 
# # Create a tidy data frame of correlations
# tidy_cors <-  d2 |> 
#   corrr::correlate()  |> 
#   corrr::stretch()
# 
# # Convert correlations stronger than some value
# # to an undirected graph object
# graph_cors <- tidy_cors |>
#  dplyr::filter(abs(r) > .2) |>
#   igraph::graph_from_data_frame(directed = FALSE)
# 
# # Plot
# ggraph(graph_cors) +
#   geom_edge_link(aes(edge_alpha = abs(r),
#                      edge_width = abs(r), 
#                      color = r)) +
#   guides(edge_alpha = "none", 
#          edge_width = "none") +
#   scale_edge_colour_gradientn(limits = c(-1, 1), 
#                               # colors = c("firebrick2",
#                               #            "dodgerblue2")
#                               colors = c("blue", "gray90",  "red")
#   ) +
#   geom_node_point(color = "gray90", 
#                   size = 7) +
#   geom_node_text(aes(label = name), 
#                  repel = TRUE) + 
#   unhcrthemes::theme_unhcr( font_size= 18)  +  
#   theme(panel.grid.major.x  = element_blank(), 
#         panel.grid.major.y  = element_blank(), 
#         panel.grid.minor = element_blank(), 
#         axis.text.x =  element_blank(), 
#         axis.text.y = element_blank(), 
#         legend.key.height= unit(0.5, 'cm'),
#         legend.key.width= unit(3, 'cm') ) +
#   labs(
#     y = "",
#     x = " ",
#     title = paste0("How much different types of Assistance aggregated at Case level are associated in ", ctr, "?"),
#     subtitle = paste0("Correlation analysis: Red color indicate a positive association, while blue a negative one "),
#     caption = paste0("Source: Data available in RIDL @ ", ridl, 
#                      "")
#   )
}

```


```{r examples-plot_assist_combin, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

plot_assist_combin(progres = progres,
                                    ctr = "Ecuador",
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 )

```

```{r tests-plot_assist_combin}

```


### 5.4 Targeting of cash assistance 

```{r function-plot_assist_cashtarget}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
plot_assist_cashtarget  <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) {
  
RegistrationGroupall <-  as.data.frame(progres[17]) 

#names(RegistrationGroupall)
model_logitCash <- glm(assistance_cash_bol ~
          ## test predictors below
                      group_size1 + 
                      ratio_female_cat + 
                     ratio_dependant_cat + 
                     sex_fp + 
                     age_avg_cat + 
                     age_sd_cat + 
                     divorced_separated_widow + 
                     single_adult + 
                     married_engaged +
                     single_minor + 
                     child_at_risk +
                     disability + 
                     serious_medical_condition +
                     sgbv,  
                     
                   data= RegistrationGroupall, 
                   family = binomial)  |> 
  ## stepwise indicator selection
  # http://www.sthda.com/english/articles/36-classification-methods-essentials/150-stepwise-logistic-regression-essentials-in-r/
  MASS::stepAIC(trace = FALSE) 

#broom::tidy(model_logit)


# https://www.youtube.com/watch?v=C4N3_XJJ-jU
far <- model_logitCash$null.deviance/-2 ## McFadden's Pseudo R2
ll <- model_logitCash$deviance/-2 ## log -likelihood for the fancy model
r2 <- (far -ll) / far ## Pseudo R2
pval <-  1- pchisq(2*(ll- far), df=(length(model_logitCash$coefficients)-1))  # pvalue

tidy_forestCash <-
  model_logitCash |>
  # perform initial tidying of the model
  broom.helpers::tidy_and_attach(exponentiate = TRUE, conf.int = TRUE) |>
  # adding in the reference row for categorical variables
  broom.helpers::tidy_add_reference_rows() |>
  # adding a reference value to appear in plot
  broom.helpers::tidy_add_estimate_to_reference_rows() |>
  # adding the variable labels
  broom.helpers::tidy_add_term_labels() |>
  # removing intercept estimate from model
  broom.helpers::tidy_remove_intercept()



tidy_forestCash2 <- tidy_forestCash |>
  # removing variable if pvalue are more than 0.4
  dplyr::filter( p.value < 0.3)

#tidy_forest

p <- tidy_forestCash2 |>
  mutate(
    plot_label = paste(var_label, label, sep = ":") |> 
      forcats::fct_inorder() |>
      forcats::fct_rev()
  ) |>
  ggplot(aes(x = plot_label, 
             y = estimate, 
             ymin = conf.low, 
             ymax = conf.high, 
             color = variable)) +
  geom_hline(yintercept = 1, linetype = 2) +
  geom_pointrange() +
  coord_flip() +
  theme(legend.position = "none") +    
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.y = element_text(size = 10)) +
  labs(
    y = "Odds Ratio",
    x = " ",
    title = "What are the criteria predicting those receiving cash assistance?",
    subtitle = paste0("Regression analysis based on records in ", ctr, " analysed at case level."),
    caption = paste0("Source: Data available in RIDL @ ", ridl,"\n",
              str_wrap( "An odds ratio measures the association between a predictor variable (x) and the outcome variable (y). It represents the ratio of the odds that an event will occur (event = 1) given the presence of the predictor x (x = 1), compared to the odds of the event occurring in the absence of that predictor (x = 0).",180),
              "\n",
              str_wrap( paste0("McFadden's Pseudo R2 is ", far, 
                          "; log -likelihood for the fancy model is ", ll,
                          "; Pseudo R2 is ", r2,
                          " and its p-value is ", pval),180) ))

return(p)
}

```


```{r examples-plot_assist_cashtarget, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

# progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
# progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")

# plot_assist_cashtarget(progres = progres,
#                                     ctr = "Ecuador",
#                                     ridl = "data-should-be-on-ridl",
#                                     thisyear = 2021 )
```

```{r tests-plot_assist_cashtarget}

```


### 5.5 Who did not get any single assistance record?
 
```{r function-plot_assist_nothing}
#' @title Assemble all data components in a list and compute indicators
#' @description The function compute a summary chart 
#' @param progres   a list with all required frame re-encoded
#' @param ctr Country or Business Unit for the dataset dump
#' @param year Year of reference
#' @param ridl  name of the project in ridl.unhcr.org, the internal UNHCR repository based on CKAN
#' @return a list with both a ggplot2 crafted chart and the summary data
#' @export 
#'
#'

plot_assist_nothing  <- function(progres,
                                    ctr, 
                                    ridl = "data-should-be-on-ridl",
                                    thisyear = 2021 ) { 
  
 RegistrationGroupall <-  as.data.frame(progresobj[17]) 
 # names(RegistrationGroupall)
 # table( RegistrationGroupall$got_assistance, useNA = "ifany")
 
 
 model_logit <- glm(got_assistance ~ 
          ## test predictors below
                      group_size1 + 
                      ratio_female_cat + 
                     ratio_dependant_cat + 
                     sex_fp + 
                     age_avg_cat + 
                     age_sd_cat + 
                     divorced_separated_widow + 
                     single_adult + 
                     married_engaged +
                     single_minor + 
                     child_at_risk +
                     disability + 
                     serious_medical_condition +
                     sgbv,  
                   data= RegistrationGroupall, 
                   family = binomial)  |> 
  ## stepwise indicator selection
  # http://www.sthda.com/english/articles/36-classification-methods-essentials/150-stepwise-logistic-regression-essentials-in-r/
  MASS::stepAIC(trace = FALSE) 

#broom::tidy(model_logit)




## Key indicator on model
# https://www.youtube.com/watch?v=C4N3_XJJ-jU
far <- model_logit$null.deviance/-2 ## McFadden's Pseudo R2
ll <- model_logit$deviance/-2 ## log -likelihood for the fancy model
r2 <- (far -ll) / far ## Pseudo R2
pval <-  1- pchisq(2*(ll- far), df=(length(model_logit$coefficients)-1))  # pvalue


tidy_forest <-
  model_logit |>
  # perform initial tidying of the model
  broom.helpers::tidy_and_attach(exponentiate = TRUE, conf.int = TRUE) |>
  # adding in the reference row for categorical variables
  broom.helpers::tidy_add_reference_rows() |>
  # adding a reference value to appear in plot
  broom.helpers::tidy_add_estimate_to_reference_rows() |>
  # adding the variable labels
  broom.helpers::tidy_add_term_labels() |>
  # removing intercept estimate from model
  broom.helpers::tidy_remove_intercept()
#tidy_forest


tidy_forest2 <- tidy_forest |>
  # removing variable if pvalue are more than 0.4
  dplyr::filter( p.value < 0.3)


p <- tidy_forest2 |>
  mutate(
    plot_label = paste(var_label, label, sep = ":") |> 
      forcats::fct_inorder() |>
      forcats::fct_rev() ) |>
  ggplot(aes(x = plot_label, 
             y = estimate, 
             ymin = conf.low, 
             ymax = conf.high, 
             color = variable)) +
  geom_hline(yintercept = 1, linetype = 2) +
  geom_pointrange() +
  coord_flip() +
  theme(legend.position = "none") +    
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  unhcrthemes::theme_unhcr( font_size= 18)  +  
  theme(panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.major.y  = element_blank(), 
        panel.grid.minor = element_blank(),  
        axis.text.y = element_text(size = 10)) +
  labs(
    y = "Odds Ratio",
    x = " ",
    title = "Factors predicting Cases that did not get records Assistance",
    subtitle = paste0("Regression analysis "),
    caption = paste0("Source: Data available in RIDL @ ", ridl, "\n",
         str_wrap( "An odds ratio measures the association between a predictor variable (x) and the outcome variable (y). It represents the ratio of the odds that an event will occur (event = 1) given the presence of the predictor x (x = 1), compared to the odds of the event occurring in the absence of that predictor (x = 0).",180),"\n",
              "\n",
              str_wrap( paste0("McFadden's Pseudo R2 is ", far, 
                          "; log -likelihood for the fancy model is ", ll,
                          "; Pseudo R2 is ", r2,
                          " and its p-value is ", pval),180) ))
return(p)
}
```

 

```{r examples-plot_assist_nothing, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

# progresobj <- data_load(dataraw = system.file("demo/", package = "proGresAnalysis") )
# progres <- data_recode(progresobj = progresobj,  ctr = "Ecuador")
# plot_assist_nothing (progres = progres,
#                                     ctr = "Ecuador",
#                                     ridl = "data-should-be-on-ridl",
#                                     thisyear = 2021 ) 

```

```{r tests-plot_assist_nothing}

```





 
 


```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Chart Library")
pkgdown::build_site()
```

